---
title: "nn_corr_multilevel_fisherz_vIT_revision_perlayer"
author: "Anonymous"
date: "2023-06-16"
output: html_document
---
---
title: "iclr_corr"
author: "Anonymous"
date: '2022-11-11'
output:
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---

""" This notebook examines whether the correlation coefficients between
two metrics are statistically significant or not.

Factors: \* functionality: 1) ablation impact 2) decoding accuracy \*
metrics: 1) cka 2) mean_cca-Corr 3) mean_sq_cca_corr 4) procrustes 5)
pwcca

Methods:

-   linear model of correlation coefficient (different from 0), modeling
    random intercepts for class and layer
-   I use fisher z to transform these correlation coefficients into Z
    vlaues (normal distribution)
-   From that, we get the t-estimate, testing whether this is
    significant
-   Afterward, I plan to convert the B0 estimate back into an r value,
    which is interpretable.

TODO: concatenate all .csv files make sure that the factor information
is inserted into each """ \# load data \# calculate correlation \#
fisher z transform \# model mean cor value for class layer unit

## libraries
```{r load libraries, include=FALSE}
library(psych)
library(car)
#library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)
library(dplyr)
library(correlation)
library(ggplot2)
library(rmarkdown)
library(readr)
library(yaml)
library(tidyverse)
library(GGally)
library(DescTools)
library(gghalves)
library(ggpubr)
library(extrafont)
library(gridExtra)
library(patchwork)
library(DescTools)

# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

```{r figure save parameters}
font_import(pattern = "DejaVu", prompt = FALSE)
myFont <- "DejaVu Sans Mono"
w = 3
h = 1.8
units = c("in")
dpi = 600
scale = 2.5
```

# load data 
```{r concatenate dataframe}
main_dir <- dirname(getwd())
main_dir <- "/Users/h/Dropbox/projects_dropbox/other_sideprojects/iclr/third_revision"
model = 'vit'
concat_df = data.frame()
  for (dv in c('vit_ablation_impact_X_cka', 
               'vit_ablation_impact_X_mean_cca_corr', 
               'vit_ablation_impact_X_mean_sq_cca_corr',
               'vit_ablation_impact_X_procrustes', 
               'vit_ablation_impact_X_pwcca',
               'vit_decoding_accuracy_delta_X_cka',
               'vit_decoding_accuracy_delta_X_mean_cca_corr',
               'vit_decoding_accuracy_delta_X_mean_sq_cca_corr',
               'vit_decoding_accuracy_delta_X_procrustes', 
               'vit_decoding_accuracy_delta_X_pwcca')) {
  if (model == "alexnet") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
  } else if (model == "mobilenet") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '-mobilenet.csv'))
  } else if (model == "vit") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
  }
  
df <- read.csv(data_fname)
newdv <- sub("^vit_", "", dv)
df$functionality <- strsplit(newdv, '_X_')[[1]][1]
df$metric <- strsplit(newdv, '_X_')[[1]][2]
concat_df <- rbind(concat_df, df)
}

```
```{r}
concat_df$layerX <- concat_df$class
concat_df$classX <- concat_df$layer
concat_df$class <- concat_df$classX
concat_df$layer <- concat_df$layerX
```


# load data

```{r reverse code and contrast code}
concat_df = concat_df %>% mutate(corr_transform = ifelse(metric == "mean_cca_corr" | metric == "mean_sq_cca_corr", -1 * correlation, correlation))
```

```{r fisher z transform}
N <- concat_df %>%
  group_by(class ,layer, functionality)  %>%
  mutate(fisherz = DescTools::FisherZ(corr_transform))
average_fisherz <- meanSummary(N,
                         c("class", "layer", "functionality"), "fisherz")
average_fisherz$fisherz <- average_fisherz$mean_per_sub
average_fisherz$corr_z = DescTools::FisherZInv(average_fisherz$fisherz)

```

1)  transformed mean_cca_corr mean_sq_cca_corr inverse
2)  fisher z for correlations
3)  within class/functionality/layers
4)  average

```{r contrast code}
average_fisherz$func_con[average_fisherz$functionality == "ablation_impact"] <- -0.5
average_fisherz$func_con[average_fisherz$functionality == "decoding_accuracy_delta"] <- 0.5

average_fisherz$func  = factor(average_fisherz$functionality)
average_fisherz$layer_ordered <- factor(average_fisherz$layer, 
                                   levels=c( "encoder.layers.encoder_layer_0",  "encoder.layers.encoder_layer_1" , "encoder.layers.encoder_layer_2" , "encoder.layers.encoder_layer_3",  "encoder.layers.encoder_layer_4",  "encoder.layers.encoder_layer_5",  "encoder.layers.encoder_layer_6",  "encoder.layers.encoder_layer_7",  "encoder.layers.encoder_layer_8", "encoder.layers.encoder_layer_9",  "encoder.layers.encoder_layer_10", "encoder.layers.encoder_layer_11"))
average_fisherz$layer_con  = factor(average_fisherz$layer_ordered)

contrasts(average_fisherz$layer_con) = contr.helmert(12)
```

# Multilevel modeling
```{r multilevel modeling }
full = lmer(corr_z ~ func_con * layer_con + (1|class)   , data = average_fisherz)
summary(full)
```

# pairwisee
```{r}
library(emmeans)
emmeans(full, list(pairwise ~ layer_con* func_con), adjust = "tukey")
```

```{r}
Anova(full, type = "III", test.statistic = "F")
```

```{r raincloudplots main effect of functionality}
# parameters __________________________________________________________________
model = 'vit'
model_keyword = "ViT"
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "func_layer"
ylim = c(-.25, .8)
se = "se"
subject = "class"
ggtitle = paste0(model_keyword,
                 " :: Functionality, averaged across layers and classes")
legend_title = "Functionality"
xlab = "Functionality "
ylab = "Correlation between \nmetric and functionality"

dv_keyword = "corr"

classwise <- meanSummary(average_fisherz,
                         c(subject, iv), "corr_z")

groupwise <- summarySEwithin(
  data = classwise,
  measurevar = "mean_per_sub",
  withinvars = c(iv),
  idvar = subject
)

subjectwise = classwise
color <- c("#D73027", "#4575B4")
# if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
#   color <- c("#1B9E77", "#D95F02")
# } else {
#   color <- c("#D73027", "#4575B4")
# }

# ggplot ______________________________________________________________________
p1 <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',
    adjust = 1.5,
    trim = FALSE,
    alpha = .3,
    colour = NA
  ) +
  
  geom_line(data = subjectwise,
    aes(
      group = .data[[subject]],
      x = as.numeric(.data[[iv]]) - .15,
      y = .data[[subjectwise_mean]],
      fill = factor(.data[[iv]])
      ),
    linetype = "solid",
    color = "grey",
    alpha = .3) +

  geom_point(
    aes(
      x = as.numeric(.data[[iv]]) - .15,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .1,
    colour = "black",
    errorbar.draw = FALSE
  ) +
  
  # legend stuff ________________________________________________________
  
  guides(color = "none") +
  guides(fill = guide_legend(title = legend_title)) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  scale_x_discrete(
    labels = c(
      "ablation_impact" = "Network performance deficits",
      "decoding_accuracy_delta" = "Decoding accuracy deficits"
    )
  ) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ylim) +
  theme_bw() + theme_classic2() +
  theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=12))

save_fname <-
  file.path(main_dir,
            'results',
            'figure',
            paste0(model, '01_iv-', iv, '_dv-', dv_keyword, '.png'))
ggsave(
  save_fname,
  width = w,
  unit = "in",
  dpi = 600,
  scale = 2.5
)
p1
```

```{r raincloudplots main effect of layer}
# parameters __________________________________________________________________
metric_classwise <- meanSummary(
        average_fisherz,
        c("class","layer_con"), "corr_z"
    )

metric_groupwise <- summarySEwithin(
        data = metric_classwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c( "layer_con"), # iv
        idvar = "class"
    )

subjectwise = metric_classwise
groupwise = metric_groupwise
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "layer_con"
ylim = c(0, .5)
se = "se"
subject = "class"
ggtitle = paste0(model_keyword, " :: average value across metrics and functionality")
legend_title = "layer"
xlab = "Layer"
ylab = "Correlation between \nlayer and functionality"
iv_keyword = "layer"
dv_keyword = "corr"
color <- c( "#FFECC9", "#F3D7C4", "#E6C1BF", "#DAACB9", "#CE96B4", "#C281AF", "#B56BAA", "#A956A5", "#9D40A0", "#912B9A", "#841595", "#780090")

# ggplot ______________________________________________________________________
p2 <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',
    adjust = 1.5,
    trim = TRUE,
    alpha = .3,
    colour = NA
  ) +
  
  geom_point(
    aes(
      x = as.numeric(factor(.data[[iv]])) - .15 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .2,
    colour = "black",
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE, 
    errorbar.draw = FALSE
  ) +
  
  # legend stuff ________________________________________________________ # nolint

  guides(fill = guide_legend(override.aes = list(shape = 20, size = 1, alpha = 1))) +
           theme(legend.title = legend_title) +
  scale_shape(guide=FALSE) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ylim) +
  theme_bw() + theme_classic2() +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  )) +
  theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=12))
save_fname <-
  file.path(main_dir,
            'results',
            'figure',
            paste0(model, '02_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))
ggsave(
  save_fname,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5
)

p2
```
# check nan values
```{r}
# check nan
rows_with_nans <- apply(average_fisherz, 1, function(row) any(is.na(row)))

# Print the rows with NaNs
print(average_fisherz[rows_with_nans, ])

# Remove rows with NaN values
average_fisherz_dropna <- average_fisherz[complete.cases(average_fisherz), ]

# Print the resulting dataframe
print(average_fisherz_dropna)
```

# ggplot interaction
```{r raincloudplots interaction}
library(gghalves)

# parameters __________________________________________________________________
average_fisherz_dropna$func = average_fisherz_dropna$functionality
int_unitwise <- meanSummary(
        average_fisherz_dropna,
        c("class", "func", "layer_ordered"), "corr_z"
    )

int_groupwise <- summarySEwithin(
        data = int_unitwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("func", "layer_ordered"), # iv
        idvar = "class"
    )

subjectwise = int_unitwise
subjectwise$layer_ordered <- factor(
  subjectwise$layer_ordered,
  levels = c(
    "encoder.layers.encoder_layer_0",
    "encoder.layers.encoder_layer_1" ,
    "encoder.layers.encoder_layer_2" ,
    "encoder.layers.encoder_layer_3",
    "encoder.layers.encoder_layer_4",
    "encoder.layers.encoder_layer_5",
    "encoder.layers.encoder_layer_6",
    "encoder.layers.encoder_layer_7",
    "encoder.layers.encoder_layer_8",
    "encoder.layers.encoder_layer_9",
    "encoder.layers.encoder_layer_10",
    "encoder.layers.encoder_layer_11"
  )
)
subjectwise$varint <-
  as.factor(paste(subjectwise$layer_ordered, subjectwise$func))
subjectwise$varint <- factor(
  subjectwise$varint,
  levels =  c(
    "encoder.layers.encoder_layer_0 ablation_impact",
"encoder.layers.encoder_layer_1 ablation_impact",
"encoder.layers.encoder_layer_2 ablation_impact",
"encoder.layers.encoder_layer_3 ablation_impact",
"encoder.layers.encoder_layer_4 ablation_impact",
"encoder.layers.encoder_layer_5 ablation_impact",
"encoder.layers.encoder_layer_6 ablation_impact",
"encoder.layers.encoder_layer_7 ablation_impact",
"encoder.layers.encoder_layer_8 ablation_impact",
"encoder.layers.encoder_layer_9 ablation_impact",
"encoder.layers.encoder_layer_10 ablation_impact",
# "encoder.layers.encoder_layer_11 ablation_impact",
"encoder.layers.encoder_layer_0 decoding_accuracy_delta",
"encoder.layers.encoder_layer_1 decoding_accuracy_delta",
"encoder.layers.encoder_layer_2 decoding_accuracy_delta",
"encoder.layers.encoder_layer_3 decoding_accuracy_delta",
"encoder.layers.encoder_layer_4 decoding_accuracy_delta",
"encoder.layers.encoder_layer_5 decoding_accuracy_delta",
"encoder.layers.encoder_layer_6 decoding_accuracy_delta",
"encoder.layers.encoder_layer_7 decoding_accuracy_delta",
"encoder.layers.encoder_layer_8 decoding_accuracy_delta",
"encoder.layers.encoder_layer_9 decoding_accuracy_delta",
"encoder.layers.encoder_layer_10 decoding_accuracy_delta",
"encoder.layers.encoder_layer_11 decoding_accuracy_delta"
  )
)
groupwise = int_groupwise
iv1 = "func"
iv2 = "layer_ordered" 
sub_mean = "mean_per_sub" 
group_mean = "mean_per_sub_norm_mean" 
se = "se" ; subject = "class"
ggtitle = paste0(model_keyword," :: Interaction of functionality and layer" )

legend_title = "Layer"
xlab = "Functionality"
ylab = "Correlation between \nlayer and functionality"
iv_keyword = "funcXlayer"
dv_keyword = "corr"

int_color = c("#FFECC9", "#FFDBB5", "#FEC9A1", "#FEB88D", "#FEA779", "#FE9665", "#FD8450", "#FD733C", "#FD6228", "#FC5014", "#FC3F00",
              # decoding 12 conditions
         "#FFECC9", "#EFD7CE", "#DEC1D2", "#CEACD7", "#BE96DC", "#AE81E0", "#9D6BE5", "#8D56E9", "#7D40EE", "#6D2BF3", "#5C15F7", "#4C00FC"
)

bw_color = c("#0F0F0F", "#494949", "#838383", "#BDBDBD", "#F7F7F7", "#BDBDBD", "#F7F7F7","#838383", "#BDBDBD", "#BDBDBD")
p3 <- ggplot(data = subjectwise,
            aes(y = .data[[sub_mean]],
                x = .data[[iv1]],
                fill =varint,
                width=.9)) +
  geom_half_violin(
    aes(fill = varint),#.data[[iv2]]),
    position = position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = 0,
    colour = NA
  ) +

  geom_point(
    data = subjectwise,
    aes(
      x = .data[[iv1]],
      y = .data[[sub_mean]],
      color = varint
    ),
    position = position_jitterdodge(), 
    size = 2,
    alpha = 0.8,
    shape = 20, 
    show.legend=FALSE
  ) +

  geom_half_boxplot(
    data = subjectwise,
    aes(x = .data[[iv1]],
        y = .data[[sub_mean]],
        fill = varint),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .8,
    colour = "black",
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE,
    errorbar.draw = FALSE,
    center = TRUE,
    show.legend=TRUE
  ) +

  # legend stuff __________________________________________________________________________________ # nolint

  scale_fill_manual(values = int_color, name = "metric", guide = "none") +
  scale_color_manual( values = int_color, name = "metric", guide = "none") +

  guides(fill = "none") +
  guides(color = "none") +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
    scale_x_discrete(
    labels = c(
      "ablation_impact" = "Network performance deficits",
      "decoding_accuracy_delta" = "Decoding accuracy deficits"
    )
  ) +

  theme_bw() + theme_classic2() +
    #theme(aspect.ratio=4/6) 
theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=14))


p3

p3
save_fname <-
  file.path(main_dir,
            'results',
            'figure',
            paste0(model, '03_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))


ggsave(
  save_fname,
  plot = p3,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5)
```

# ggplot interaction
```{r raincloudplots interaction}
library(gghalves)

# parameters __________________________________________________________________
average_fisherz_dropna$func = average_fisherz_dropna$functionality
int_unitwise <- meanSummary(
        average_fisherz_dropna,
        c("class", "func", "layer_ordered"), "corr_z"
    )

int_groupwise <- summarySEwithin(
        data = int_unitwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("func", "layer_ordered"), # iv
        idvar = "class"
    )

subjectwise = int_unitwise
subjectwise$layer_ordered <- factor(
  subjectwise$layer_ordered,
  levels = c(
    "encoder.layers.encoder_layer_0",
    "encoder.layers.encoder_layer_1" ,
    "encoder.layers.encoder_layer_2" ,
    "encoder.layers.encoder_layer_3",
    "encoder.layers.encoder_layer_4",
    "encoder.layers.encoder_layer_5",
    "encoder.layers.encoder_layer_6",
    "encoder.layers.encoder_layer_7",
    "encoder.layers.encoder_layer_8",
    "encoder.layers.encoder_layer_9",
    "encoder.layers.encoder_layer_10",
    "encoder.layers.encoder_layer_11"
  )
)
subjectwise$varint <-
  as.factor(paste(subjectwise$layer_ordered, subjectwise$func))
subjectwise$varint <- factor(
  subjectwise$varint,
  levels =  c(
    "encoder.layers.encoder_layer_0 ablation_impact",
"encoder.layers.encoder_layer_1 ablation_impact",
"encoder.layers.encoder_layer_2 ablation_impact",
"encoder.layers.encoder_layer_3 ablation_impact",
"encoder.layers.encoder_layer_4 ablation_impact",
"encoder.layers.encoder_layer_5 ablation_impact",
"encoder.layers.encoder_layer_6 ablation_impact",
"encoder.layers.encoder_layer_7 ablation_impact",
"encoder.layers.encoder_layer_8 ablation_impact",
"encoder.layers.encoder_layer_9 ablation_impact",
"encoder.layers.encoder_layer_10 ablation_impact",
# "encoder.layers.encoder_layer_11 ablation_impact",
"encoder.layers.encoder_layer_0 decoding_accuracy_delta",
"encoder.layers.encoder_layer_1 decoding_accuracy_delta",
"encoder.layers.encoder_layer_2 decoding_accuracy_delta",
"encoder.layers.encoder_layer_3 decoding_accuracy_delta",
"encoder.layers.encoder_layer_4 decoding_accuracy_delta",
"encoder.layers.encoder_layer_5 decoding_accuracy_delta",
"encoder.layers.encoder_layer_6 decoding_accuracy_delta",
"encoder.layers.encoder_layer_7 decoding_accuracy_delta",
"encoder.layers.encoder_layer_8 decoding_accuracy_delta",
"encoder.layers.encoder_layer_9 decoding_accuracy_delta",
"encoder.layers.encoder_layer_10 decoding_accuracy_delta",
"encoder.layers.encoder_layer_11 decoding_accuracy_delta"
  )
)
groupwise = int_groupwise
iv1 = "func"
iv2 = "layer_ordered" 
sub_mean = "mean_per_sub" 
group_mean = "mean_per_sub_norm_mean" 
se = "se" ; subject = "class"
ggtitle = paste0(model_keyword," :: Interaction of functionality and layer" )

legend_title = "Layer"
xlab = "Functionality"
ylab = "Correlation between \nlayer and functionality"
iv_keyword = "funcXlayer"
dv_keyword = "corr"

int_color = c("#FFECC9", "#FFDBB5", "#FEC9A1", "#FEB88D", "#FEA779", "#FE9665", "#FD8450", "#FD733C", "#FD6228", "#FC5014", "#FC3F00",
              # decoding 12 conditions
         "#FFECC9", "#EFD7CE", "#DEC1D2", "#CEACD7", "#BE96DC", "#AE81E0", "#9D6BE5", "#8D56E9", "#7D40EE", "#6D2BF3", "#5C15F7", "#4C00FC"
)

bw_color = c("#0F0F0F", "#494949", "#838383", "#BDBDBD", "#F7F7F7", "#BDBDBD", "#F7F7F7","#838383", "#BDBDBD", "#BDBDBD")
p3 <- ggplot(data = subjectwise,
            aes(y = .data[[sub_mean]],
                x = .data[[iv1]],
                fill =varint,
                width=.9)) +
  geom_half_violin(
    aes(fill = varint),#.data[[iv2]]),
    position = position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = 0,
    colour = NA
  ) +

  geom_point(
    data = subjectwise,
    aes(
      x = .data[[iv1]],
      y = .data[[sub_mean]],
      color = varint
    ),
    position = position_jitterdodge(), 
    size = 2,
    alpha = 0.8,
    shape = 20, 
    show.legend=FALSE
  ) +

  geom_half_boxplot(
    data = subjectwise,
    aes(x = .data[[iv1]],
        y = .data[[sub_mean]],
        fill = varint),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .8,
    colour = "black",
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE,
    errorbar.draw = FALSE,
    center = TRUE,
    show.legend=TRUE
  ) +

  # legend stuff __________________________________________________________________________________ # nolint

  scale_fill_manual(values = int_color, name = "metric", guide = "none") +
  scale_color_manual( values = int_color, name = "metric", guide = "none") +

  guides(fill = "none") +
  guides(color = "none") +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
    scale_x_discrete(
    labels = c(
      "ablation_impact" = "Network performance deficits",
      "decoding_accuracy_delta" = "Decoding accuracy deficits"
    )
  ) +

  theme_bw() + theme_classic2() +
    #theme(aspect.ratio=4/6) 
theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=14))


p3

p3
save_fname <-
  file.path(main_dir,
            'results',
            'figure',
            paste0(model, '03_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))


ggsave(
  save_fname,
  plot = p3,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5)
```

## ggplot metrix X layer X functionality
```{r concatenate dataframe}
main_dir <- dirname(getwd())
main_dir <- "/Users/h/Dropbox/projects_dropbox/other_sideprojects/iclr/third_revision"
model = 'vit'
concat_df = data.frame()
  for (dv in c('vit_ablation_impact_X_cka', 
               'vit_ablation_impact_X_mean_cca_corr', 
               'vit_ablation_impact_X_mean_sq_cca_corr',
               'vit_ablation_impact_X_procrustes', 
               'vit_ablation_impact_X_pwcca',
               'vit_decoding_accuracy_delta_X_cka',
               'vit_decoding_accuracy_delta_X_mean_cca_corr',
               'vit_decoding_accuracy_delta_X_mean_sq_cca_corr',
               'vit_decoding_accuracy_delta_X_procrustes', 
               'vit_decoding_accuracy_delta_X_pwcca')) {
  if (model == "alexnet") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
  } else if (model == "mobilenet") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '-mobilenet.csv'))
  } else if (model == "vit") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
  }
  
df <- read.csv(data_fname)
newdv <- sub("^vit_", "", dv)
df$functionality <- strsplit(newdv, '_X_')[[1]][1]
df$metric <- strsplit(newdv, '_X_')[[1]][2]
concat_df <- rbind(concat_df, df)
}

concat_df$layerX <- concat_df$class
concat_df$classX <- concat_df$layer
concat_df$class <- concat_df$classX
concat_df$layer <- concat_df$layerX

concat_df = concat_df %>% mutate(corr_transform = ifelse(metric == "mean_cca_corr" | metric == "mean_sq_cca_corr", -1 * correlation, correlation))
# parameters __________________________________________________________________
for (metric in c("cka","mean_cca_corr","mean_sq_cca_corr","procrustes","pwcca"  ) ) {
  print(metric)
  
}
```


```{r concatenate dataframe}
model_keyword = "ViT"
N <- concat_df %>%
  group_by(class ,layer, functionality)  %>%
  mutate(fisherz = DescTools::FisherZ(corr_transform))
average_fisherz <- meanSummary(N,
                         c("class", "layer","metric", "functionality"), "fisherz")
average_fisherz$fisherz <- average_fisherz$mean_per_sub
average_fisherz$corr_z = DescTools::FisherZInv(average_fisherz$fisherz)

average_fisherz$func_con[average_fisherz$functionality == "ablation_impact"] <- -0.5
average_fisherz$func_con[average_fisherz$functionality == "decoding_accuracy_delta"] <- 0.5

average_fisherz$func  = factor(average_fisherz$functionality)
average_fisherz$layer_ordered <- factor(average_fisherz$layer, 
                                   levels=c( "encoder.layers.encoder_layer_0",  "encoder.layers.encoder_layer_1" , "encoder.layers.encoder_layer_2" , "encoder.layers.encoder_layer_3",  "encoder.layers.encoder_layer_4",  "encoder.layers.encoder_layer_5",  "encoder.layers.encoder_layer_6",  "encoder.layers.encoder_layer_7",  "encoder.layers.encoder_layer_8", "encoder.layers.encoder_layer_9",  "encoder.layers.encoder_layer_10", "encoder.layers.encoder_layer_11"))
average_fisherz$layer_con  = factor(average_fisherz$layer_ordered)

contrasts(average_fisherz$layer_con) = contr.helmert(12)

for (metric in c("cka","mean_cca_corr","mean_sq_cca_corr","procrustes","pwcca"  ) ) {
  print(metric)
  subset_df = average_fisherz[average_fisherz$metric == metric,]



int_unitwise <- meanSummary(
        subset_df,
        c("class", "func", "layer_ordered"), "corr_z"
    )

int_groupwise <- summarySEwithin(
        data = int_unitwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("func", "layer_ordered"), # iv
        idvar = "class"
    )

test_subjectwise = int_unitwise
test_subjectwise$varint <-
  as.factor(paste(test_subjectwise$layer_ordered, test_subjectwise$func))
test_subjectwise$varint <- factor(
  test_subjectwise$varint,
  levels =  c(
    "encoder.layers.encoder_layer_0 ablation_impact",
"encoder.layers.encoder_layer_1 ablation_impact",
"encoder.layers.encoder_layer_2 ablation_impact",
"encoder.layers.encoder_layer_3 ablation_impact",
"encoder.layers.encoder_layer_4 ablation_impact",
"encoder.layers.encoder_layer_5 ablation_impact",
"encoder.layers.encoder_layer_6 ablation_impact",
"encoder.layers.encoder_layer_7 ablation_impact",
"encoder.layers.encoder_layer_8 ablation_impact",
"encoder.layers.encoder_layer_9 ablation_impact",
"encoder.layers.encoder_layer_10 ablation_impact",
"encoder.layers.encoder_layer_11 ablation_impact",
"encoder.layers.encoder_layer_0 decoding_accuracy_delta",
"encoder.layers.encoder_layer_1 decoding_accuracy_delta",
"encoder.layers.encoder_layer_2 decoding_accuracy_delta",
"encoder.layers.encoder_layer_3 decoding_accuracy_delta",
"encoder.layers.encoder_layer_4 decoding_accuracy_delta",
"encoder.layers.encoder_layer_5 decoding_accuracy_delta",
"encoder.layers.encoder_layer_6 decoding_accuracy_delta",
"encoder.layers.encoder_layer_7 decoding_accuracy_delta",
"encoder.layers.encoder_layer_8 decoding_accuracy_delta",
"encoder.layers.encoder_layer_9 decoding_accuracy_delta",
"encoder.layers.encoder_layer_10 decoding_accuracy_delta",
"encoder.layers.encoder_layer_11 decoding_accuracy_delta"
  )
)
test_groupwise = int_groupwise
iv1 = "func"
iv2 = "layer_ordered" 
sub_mean = "mean_per_sub" 
group_mean = "mean_per_sub_norm_mean" 
se = "se" ; subject = "class"
ggtitle = paste0(model_keyword," :: ", metric, " :: Interaction of functionality and layer" )

legend_title = "Layer"
xlab = "Functionality"
ylab = "Correlation between \nRDM and functionality"
iv_keyword = "funcXlayer"
dv_keyword = "corr"

int_color = c("#FFECC9", "#FFDBB5", "#FEC9A1", "#FEB88D", "#FEA779", "#FE9665", "#FD8450", "#FD733C", "#FD6228", "#FC5014", "#FC3F00","red",
              # decoding 12 conditions
         "#FFECC9", "#EFD7CE", "#DEC1D2", "#CEACD7", "#BE96DC", "#AE81E0", "#9D6BE5", "#8D56E9", "#7D40EE", "#6D2BF3", "#5C15F7", "#4C00FC"
)

bw_color = c("#0F0F0F", "#494949", "#838383", "#BDBDBD", "#F7F7F7", "#BDBDBD", "#F7F7F7","#838383", "#BDBDBD", "#BDBDBD")
# rows_with_nan <- apply(int_groupwise$mean_per_sub_mean, 1, function(row) any(is.na(row)))
# if (any(is.na(int_groupwise[["mean_per_sub_mean"]]))) {
    # If NaNs are present, remove the corresponding colors
# remove colors###########
num_nans <- which(is.na(int_groupwise[["mean_per_sub_mean"]]))
int_color <- int_color[-num_nans]
# # Drop rows with NaN values in a specific column
subjectwise <- test_subjectwise[complete.cases(test_subjectwise$mean_per_sub), , drop = FALSE]
groupwise <- test_groupwise[complete.cases(test_groupwise$mean_per_sub_mean), , drop = FALSE]
print(unique(subjectwise$varint))
# print(unique(groupwise$layer_ordered))
##########################
p3 <- ggplot(data = subjectwise,
            aes(y = .data[[sub_mean]],
                x = .data[[iv1]],
                fill = varint,
                width=.9)) +
  geom_half_violin(
    aes(fill = varint),#.data[[iv2]]),
    position = position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = 0,
    colour = NA
  ) +

  geom_point(
    data = subjectwise,
    aes(
      x = .data[[iv1]],
      y = .data[[sub_mean]],
      color = varint
    ),
    position = position_jitterdodge(), 
    size = 2,
    alpha = 0.8,
    shape = 20, 
    show.legend=FALSE
  ) +

  geom_half_boxplot(
    data = subjectwise,
    aes(x = .data[[iv1]],
        y = .data[[sub_mean]],
        fill = varint),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .8,
    colour = "black",
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE,
    errorbar.draw = FALSE,
    center = TRUE,
    show.legend=FALSE
  ) +

  # legend stuff __________________________________________________________________________________ # nolint

  # scale_fill_manual(values = int_color, name = "varint", guide = "none") +
  # scale_color_manual( values = int_color, name = "varint", guide = "none") +

  guides(fill = "none") +
  guides(color = "none") +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
  scale_x_discrete(
    labels = c(
      "ablation_impact" = "Network performance deficits",
      "decoding_accuracy_delta" = "Decoding accuracy deficits"
    )
  ) +

  theme_bw() +
  theme_classic2() +
    #theme(aspect.ratio=4/6)
theme(aspect.ratio = 6 / 10) +
  theme(
    # legend.position = "bottom",
        text = element_text(family = "DejaVu Sans"),
        plot.title = element_text(size=14)) 
#   labs(fill = "legend")


print(p3)

p3
save_fname <-
  file.path(main_dir,
            'results',
            'figure',
            paste0(model, '04_iv-', iv_keyword, '_dv-', dv_keyword, '_metric-', metric, '.png'))

w = 3
ggsave(
  save_fname,
  plot = p3,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600, 
  scale = 5)

}
```

