---
title: "iclr_corr"
author: "Heejung Jung"
date: '2022-06-09'
output:
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---

"""
This notebook examines whether the correlation coefficients between two metrics 
are statistically significant or not. 


Factors:
* functionality:
1) ablation impact 
2) decoding accuracy
* metrics: 
1) cka
2) mean_cca-Corr
3) mean_sq_cca_corr
4) procrustes
5) pwcca

Methods:
* linear model of correlation coefficient (different from 0), modeling random intercepts for class and layer
* I use fisher z to transform these correlation coefficients into Z values (normal distribution)
* From that, we get the t-estimate, testing whether this is significant
* Afterward, I plan to convert the B0 estimate back into an r value, which is interpretable. 


TODO: concatenate all .csv files
make sure that the factor information is inserted into each 
"""
# load data
# calculate correlation
# fisher z transform 
# model mean cor value for class layer unit

```{r load libraries, include=FALSE}
library(psych)
library(car)
#library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)
library(dplyr)
library(correlation)
library(ggplot2)
library(rmarkdown)
library(readr)
library(yaml)
library(tidyverse)
library(GGally)
library(DescTools)
library(gghalves)
library(ggpubr)
library(extrafont)
library(gridExtra)
library(patchwork)
library(emmeans)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
main_dir <- dirname(getwd())
file.sources = list.files(file.path(main_dir, 'utils'),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```


```{r figure save parameters, echo=FALSE, message=FALSE, warning=FALSE}
font_import(pattern = "DejaVu", prompt = FALSE)
myFont <- "DejaVu Sans Mono"
w = 3
h = 1.8
units = c("in")
dpi = 600
scale = 2.5
```

```{r concatenate dataframe}
main_dir <- dirname(getwd())
model = 'vit'
concat_df = data.frame()
  for (dv in c('vit_ablation_impact_X_cka', 
               'vit_ablation_impact_X_mean_cca_corr', 
               'vit_ablation_impact_X_mean_sq_cca_corr',
               'vit_ablation_impact_X_procrustes', 
               'vit_ablation_impact_X_pwcca',
               'vit_decoding_accuracy_delta_X_cka',
               'vit_decoding_accuracy_delta_X_mean_cca_corr',
               'vit_decoding_accuracy_delta_X_mean_sq_cca_corr',
               'vit_decoding_accuracy_delta_X_procrustes', 
               'vit_decoding_accuracy_delta_X_pwcca')) {
  if (model == "alexnet") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
  } else if (model == "mobilenet") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '-mobilenet.csv'))
  } else if (model == "vit") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
  }
  
df <- read.csv(data_fname)
newdv <- sub("^vit_", "", dv)
df$functionality <- strsplit(newdv, '_X_')[[1]][1]
df$metric <- strsplit(newdv, '_X_')[[1]][2]
concat_df <- rbind(concat_df, df)
}
```

```{r}
# swap layer and class
concat_df$layerX <- concat_df$class
concat_df$classX <- concat_df$layer
concat_df$class <- concat_df$classX
concat_df$layer <- concat_df$layerX
```

```{r reverse code and contrast code}
concat_df = concat_df %>% mutate(corr_transform = ifelse(metric == "mean_cca_corr" | metric == "mean_sq_cca_corr", -1 * correlation, correlation))
```

```{r fisher Z along layer}
concat_df$fisherz = DescTools::FisherZ(concat_df$corr_transform)
average_fisherz <- meanSummary(concat_df,
                         c("class", "functionality", "metric"), "fisherz")
average_fisherz$fisherz <- average_fisherz$mean_per_sub
average_fisherz$corr_z = DescTools::FisherZInv(average_fisherz$fisherz)
```
1) transformed mean_cca_corr mean_sq_cca_corr inverse
2) fisher z for correlations 
3) within class/functionality/metric
3) average 
```{r contrast code}
average_fisherz$func_con[average_fisherz$functionality == "ablation_impact"] <- -0.5
average_fisherz$func_con[average_fisherz$functionality == "decoding_accuracy_delta"] <- 0.5

average_fisherz$func  = factor(average_fisherz$functionality)
average_fisherz$metric_ordered <- factor(average_fisherz$metric, 
                                   levels=c("mean_cca_corr","mean_sq_cca_corr","pwcca","cka","procrustes"))
average_fisherz$metric_con  = factor(average_fisherz$metric_ordered)

contrasts(average_fisherz$metric_con) = contr.helmert(5)
```

```{r testing interim - without random effect}
lm.full = lm(corr_z ~ func_con * metric_con  , data = average_fisherz)
summary(lm.full)
```
```{r multilevel modeling }
concat_df$func_con[concat_df$functionality == "ablation_impact"] <- -0.5
concat_df$func_con[concat_df$functionality == "decoding_accuracy_delta"] <- 0.5

concat_df$func  = factor(concat_df$functionality)
concat_df$metric_ordered <- factor(concat_df$metric,
                                   levels=c("mean_cca_corr","mean_sq_cca_corr","pwcca","cka","procrustes"))
concat_df$metric_con  = factor(concat_df$metric_ordered)

contrasts(concat_df$metric_con) = contr.helmert(5)

```


```{r multilevel modeling }
full = lmer(corr_z ~ func_con * metric_con + (1|class)  , data = average_fisherz)
summary(full)
anova(full)
```



```{r}
Anova(full, type = "III", test.statistic = "F")
```

```{r}
library(emmeans)
emm1 = emmeans(full, specs =  ~ metric_con* func_con)

cka_mean = c(0,0,0,1/2,0, 0,0,0,1/2,0)
procrustes_mean = c(0,0,0,0,1/2, 0,0,0,0,1/2)

cka_mean_causal = c(0,0,0,1/2,0, 0,0,0,0,0)
procrustes_mean_causal = c(0,0,0,0,1/2, 0,0,0,0,0)

cka_mean_noncausal = c(0,0,0,0,0, 0,0,0,1/2,0)
procrustes_mean_noncausal = c(0,0,0,0,0, 0,0,0,0,1/2)

cca_mean = c(1/6, 1/6, 1/6, 0, 0, 1/6, 1/6, 1/6, 0, 0)
cka_pro = c(0,0,0,1/4,1/4, 0,0,0,1/4,1/4)

cca_mean_causal = c(1/3, 1/3, 1/3, 0, 0,0,0,0,0,0)
cka_pro_causal = c(0,0,0,1/2,1/2,0,0,0,0,0)

cca_mean_noncausal = c(0,0,0,0,0,1/3, 1/3, 1/3, 0, 0)
cka_pro_noncausal = c(0,0,0,0,0,  0,0,0,1/2,1/2)

int = c(1,1,1,1,1,-1,-1,-1,-1,-1)
contrast(emm1, method = list("cka/procrustes vs. mean_cca/mean_sq/pwcca on average" = cka_pro - cca_mean, 
                             "procrustes vs. cka on average" = procrustes_mean - cka_mean,
                             "procrustes vs. cka causal" = procrustes_mean_causal - cka_mean_causal,
                             "procrustes vs. cka noncausal" = procrustes_mean_noncausal - cka_mean_noncausal,
                             "within causal, cka/procrustes vs. mean_cca/mean_sq/pwcca" =  cka_pro_causal - cca_mean_causal,
                             "within noncausal, cka/procrustes vs. mean_cca/mean_sq/pwcca" = cka_pro_noncausal - cca_mean_noncausal) )
```


```{r barplot functionality}
# parameters __________________________________________________________________
model_keyword = "ViT"
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "func"
ylim = c(-.25, .8)
se = "se"
subject = "class"
ggtitle = paste0(model_keyword,
                 " :: Functionality, averaged across layers and classes")
legend_title = "Functionality"
xlab = "Functionality "
ylab = "Correlation between \nmetric and functionality"

dv_keyword = "corr"

classwise <- meanSummary(average_fisherz,
                         c(subject, iv), "corr_z")
groupwise <- summarySEwithin(
  data = classwise,
  measurevar = "mean_per_sub",
  withinvars = c(iv),
  idvar = subject
)

subjectwise = classwise

if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#D73027", "#4575B4")
}

# ggplot ______________________________________________________________________
p1 <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',
    #position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = .3,
    colour = NA
  ) +
    geom_line(data = subjectwise,
    aes(
      group = .data[[subject]],
      x = as.numeric(.data[[iv]]) - .15,
      y = .data[[subjectwise_mean]],
      fill = factor(.data[[iv]])
      ),
    linetype = "solid",
    color = "grey",
    alpha = .3) +

  geom_point(
    aes(
      x = as.numeric(.data[[iv]]) - .15,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .1,
    colour = "black",
    errorbar.draw = FALSE
  ) +
  
  # legend stuff ________________________________________________________
  
  guides(color = "none") +
  guides(fill = guide_legend(title = legend_title)) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  scale_x_discrete(
    labels = c(
      "ablation_impact" = "Causal deficit",
      "decoding_accuracy_delta" = "Non-causal Decoding"
    )
  ) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ylim) +
  theme_bw() + theme_classic2() +
  # theme(axis.text.x = element_text(
  #   angle = 45,
  #   vjust = 1,
  #   hjust = 1
  # )) +
  theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=12))

save_fname <-
  file.path(main_dir, 'figure', model, 
            paste0(model, '01_iv-', iv, '_dv-', dv_keyword, '.png'))
ggsave(
  save_fname,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5
)
p1
```





```{r barplot metric}
# parameters __________________________________________________________________
metric_classwise <- meanSummary(
        average_fisherz,
        c("class","metric_con"), "corr_z"
    )

metric_groupwise <- summarySEwithin(
        data = metric_classwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c( "metric_con"), # iv
        idvar = "class"
    )

subjectwise = metric_classwise
groupwise = metric_groupwise
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "metric_con"
ylim = c(-1, 1)
se = "se"
subject = "class"
ggtitle = paste0(model_keyword, " :: Metrics, averaged across layers and classes")
legend_title = "metric"
xlab = "Metric"
ylab = "Correlation between \nmetric and functionality"
iv_keyword = "metric"
dv_keyword = "corr"

if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#464655", "#898983","#B6B6C1", "#CECEE0", "#DEDEEF")
} else {
  color <- c( "#000000","#2D0040", "#5A0080","#8600BF","#B300FF")
}

# ggplot ______________________________________________________________________
p2 <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',#position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = TRUE,
    alpha = .3,
    colour = NA
  ) +
  
  geom_point(
    aes(
      x = as.numeric(factor(.data[[iv]])) - .15 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .1),
    size = 2,
    alpha = 0.8,
    #shape = 20
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .2,
    colour = "black",
    # staplelwd = 0,
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE, 
    errorbar.draw = FALSE
  ) +
  
  
  # legend stuff ________________________________________________________ # nolint

  guides(fill = guide_legend(override.aes = list(shape = 20, size = 1, alpha = 1))) +
           theme(legend.title = legend_title) +
  scale_shape(guide=FALSE) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ylim) +
  theme_bw() + theme_classic2() +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  )) +
  theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=12))
save_fname <-
  file.path(main_dir, 'figure', model,
            paste0(model, '02_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))
ggsave(
  save_fname,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5
)

p2
```








```{r barplot interaction}
library(gghalves)

# parameters __________________________________________________________________
int_unitwise <- meanSummary(
        average_fisherz,
        c("class", "func", "metric_ordered"), "corr_z"
    )

int_groupwise <- summarySEwithin(
        data = int_unitwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("func", "metric_ordered"), # iv
        idvar = "class"
    )

subjectwise = int_unitwise
subjectwise$metric_ordered <- factor(subjectwise$metric_ordered, levels = c("mean_cca_corr", "mean_sq_cca_corr", "pwcca", "cka", "procrustes"))
subjectwise$varint <- as.factor(paste(subjectwise$metric_ordered, subjectwise$func))
subjectwise$varint <- factor(subjectwise$varint, 
                             levels = c("mean_cca_corr ablation_impact", "mean_sq_cca_corr ablation_impact", "pwcca ablation_impact", "cka ablation_impact", "procrustes ablation_impact", 
                                        "mean_cca_corr decoding_accuracy_delta", "mean_sq_cca_corr decoding_accuracy_delta", "pwcca decoding_accuracy_delta", "cka decoding_accuracy_delta", "procrustes decoding_accuracy_delta" ))
groupwise = int_groupwise
iv1 = "func"
iv2 = "metric_ordered" 
sub_mean = "mean_per_sub" 
group_mean = "mean_per_sub_norm_mean" 
se = "se" ; subject = "class"
ggtitle = paste0(model_keyword," :: Interaction of functionality and metric" )

legend_title = "Metric"
xlab = "Functionality"
ylab = "Correlation between \nmetric and functionality"
iv_keyword = "funcXmetric"
dv_keyword = "corr"

int_color = c(
  "#000000",   "#3F0005",   "#7D000B",   "#BC0010",   "#FA0015",   
  "#000000",   "#00003F",   "#00007D",   "#0000BC",   "#0000FA"
)

bw_color = c("#0F0F0F", "#494949", "#838383", "#BDBDBD", "#F7F7F7")
  # decoding
p3 <- ggplot(data = subjectwise,
            aes(y = .data[[sub_mean]],
                x = .data[[iv1]],
                fill =varint,#.data[[iv2]],# varint, #.data[[iv2]],
                width=.9)) +
  geom_half_violin(
    aes(fill = varint),#.data[[iv2]]),
    position = position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = 0,
    colour = NA
  ) +
  geom_point(
    data = subjectwise,
    aes(
      x = .data[[iv1]],
      y = .data[[sub_mean]],
      #color = interaction(.data[[iv2]],.data[[iv1]])
      color = varint# .data[[iv2]]
    ),
    position = position_jitterdodge(), #position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    shape = 20, 
    show.legend=FALSE
  ) +
  geom_half_boxplot(
    data = subjectwise,
    aes(x = .data[[iv1]],
        y = .data[[sub_mean]],
        fill = varint),#interaction(metric_ordered,func )),
        #fill = .data[[iv2]]),
      
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .8,
    colour = "black",
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE,
    errorbar.draw = FALSE,
    center = TRUE,
    show.legend=TRUE
  ) +

  # legend stuff __________________________________________________________________________________ # nolint

  scale_fill_manual(values = int_color, name = "metric", guide = "none") +
  scale_color_manual( values = int_color, name = "metric", guide = "none") +

  guides(fill = "none") +
  guides(color = "none") +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
    scale_x_discrete(
    labels = c(
      "ablation_impact" = "Causal deficit",
      "decoding_accuracy_delta" = "Non-causal decoding"
    )
  ) +

  theme_bw() + theme_classic2() +
  theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=14))

p3
save_fname <-
  file.path(main_dir,            'figure', model,
            paste0(model, '03_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))

ggsave(
  save_fname,
  plot = p3,
  width = w,
  unit = "in",
  dpi = 600,
  scale = 2.5)
```


