---
title: "iclr_corr"
author: "Heejung Jung"
date: '2022-09-14'
output:
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---

"""
This notebook examines whether the correlation coefficients between two metrics 
are statistically significant or not. 

Factors:
* functionality:
1) ablation impact 
2) decoding accuracy
* metrics: 
1) cka
2) mean_cca-Corr
3) mean_sq_cca_corr
4) procrustes
5) pwcca

* linear model of correlation coefficient (different from 0), modeling random intercepts for class and layer
* I use fisher z to transform these correlation coefficients into Z vlaues (normal distribution)
* From that, we get the t-estimate, testing whether this is significant
* Afterward, I plan to convert the B0 estimate back into an r value, which is interpretable. 


TODO: concatenate all .csv files
make sure that the factor information is inserted into each 
"""
# load data
# calculate correlation
# fisher z transform 
# model mean cor value for class layer unit

```{r load libraries, include=FALSE}
library(psych)
library(car)
#library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)
library(dplyr)
library(correlation)
library(ggplot2)
library(rmarkdown)
library(readr)
library(yaml)
library(tidyverse)
library(GGally)
library(DescTools)
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```
```{r}

```

```{r concatenate dataframe}
main_dir <- dirname(getwd())
model = 'mobilenet'
concat_df = data.frame()
  for (dv in c('ablation_impact_X_cka', 
               'ablation_impact_X_mean_cca_corr', 
               'ablation_impact_X_mean_sq_cca_corr',
               'ablation_impact_X_procrustes', 
               'ablation_impact_X_pwcca',
               'decoding_accuracy_delta_X_cka',
               'decoding_accuracy_delta_X_mean_cca_corr',
               'decoding_accuracy_delta_X_mean_sq_cca_corr',
               'decoding_accuracy_delta_X_procrustes', 
               'decoding_accuracy_delta_X_pwcca')) {

    if (model == "alexnet") {
      data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
    } else if (model == "mobilenet") {
      data_fname <- file.path(main_dir, 'data', model, paste0(dv, '-mobilenet.csv'))
    }
df <- read.csv(data_fname)
df$functionality <- strsplit(dv, '_X_')[[1]][1]
df$metric <- strsplit(dv, '_X_')[[1]][2]
concat_df <- rbind(concat_df, df)
}
```

```{r reverse code and contrast code}


concat_df = concat_df %>% mutate(corr_transform = ifelse(metric == "mean_cca_corr" | metric == "mean_sq_cca_corr", -1 * correlation, correlation))


```

```{r fisher Z along layer}
concat_df$fisherz = DescTools::FisherZ(concat_df$corr_transform)
average_fisherz <- meanSummary(concat_df,
                         c("class", "functionality", "metric"), "fisherz")
average_fisherz$fisherz <- average_fisherz$mean_per_sub
average_fisherz$corr_z = DescTools::FisherZInv(average_fisherz$fisherz)
```

```{r contrast code}
average_fisherz$func_con[average_fisherz$functionality == "ablation_impact"] <- -0.5
average_fisherz$func_con[average_fisherz$functionality == "decoding_accuracy_delta"] <- 0.5

average_fisherz$func  = factor(average_fisherz$functionality)
average_fisherz$metric_ordered <- factor(average_fisherz$metric, 
                                   levels=c("mean_cca_corr","mean_sq_cca_corr","pwcca","cka","procrustes"))
average_fisherz$metric_con  = factor(average_fisherz$metric_ordered)

contrasts(average_fisherz$metric_con) = contr.helmert(5)
```

```{r model with fisherz inverse transformed metrics}
full = lmer(corr_z ~ func_con * metric_con + (1|class)  , data = average_fisherz)
summary(full)
```





```{r barplot functionality}
# parameters __________________________________________________________________
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "func"
ylim = c(-.5, .5)
se = "se"
subject = "class"
ggtitle = paste0(model, " :: functionality across layers and classes")
legend_title = "functionality"
xlab = "functionality "
ylab = "correlation between \nmetric and functionality"
w = 5
h = 3
dv_keyword = "correlation"

classwise <- meanSummary(average_fisherz,
                         c(subject, iv), "corr_z")
groupwise <- summarySEwithin(
  data = classwise,
  measurevar = "mean_per_sub",
  withinvars = c(iv),
  idvar = subject
)

subjectwise = classwise

if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#D73027", "#4575B4")
}

# ggplot ______________________________________________________________________
g <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',
    #position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = .3,
    colour = NA
  ) +
  
  geom_point(
    aes(
      x = as.numeric(.data[[iv]]) - .15,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .1,
    colour = "black",
    errorbar.draw = FALSE
  ) +
  
  # legend stuff ________________________________________________________
  
  guides(color = "none") +
  guides(fill = guide_legend(title = legend_title)) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  scale_x_discrete(
    labels = c(
      "ablation_impact" = "causal deficit",
      "decoding_accuracy_delta" = "non-causal decoding"
    )
  ) +
  xlab(xlab) +
  ylab(ylab) +
  
  theme_bw() + theme_classic2() +
  # theme(axis.text.x = element_text(
  #   angle = 45,
  #   vjust = 1,
  #   hjust = 1
  # )) +
  theme(aspect.ratio = 2 / 3) + 
  theme(legend.position = "none")
#ggsave(save_fname, width = w, height = h)
g
```





```{r barplot metric}
# parameters __________________________________________________________________
metric_classwise <- meanSummary(
        average_fisherz,
        c("class","metric_con"), "corr_z"
    )

metric_groupwise <- summarySEwithin(
        data = metric_classwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c( "metric_con"), # iv
        idvar = "class"
    )

subjectwise = metric_classwise
groupwise = metric_groupwise
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "metric_con"
ylim = c(0, .5)
se = "se"
subject = "class"
ggtitle = paste0(model, " :: metric across layers and classes")
legend_title = "metric"
xlab = "metric"
ylab = "correlation between \nmetric and functionality"
w = 5
h = 10
dv_keyword = "correlation"

if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#464655", "#898983","#B6B6C1", "#CECEE0", "#DEDEEF")
} else {
  color <- c( "#000000","#2D0040", "#5A0080","#8600BF","#B300FF")
}

# ggplot ______________________________________________________________________
g <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',#position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = TRUE,
    alpha = .3,
    colour = NA
  ) +
  
  geom_point(
    aes(
      x = as.numeric(factor(.data[[iv]])) - .15 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    #shape = 20
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .2,
    colour = "black",
    # staplelwd = 0,
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE, 
    errorbar.draw = FALSE
  ) +
  
  
  # legend stuff ________________________________________________________ # nolint
  #expand_limits(x = 2.8) +
  #guides(fill = "none") +
  #guides(color = "none") +
  #labs(shape = "metric", color = "metric") +
  #theme(legend.position = "none") +
  guides(fill = guide_legend(override.aes = list(shape = 20, size = 1, alpha = 1))) +
           theme(legend.title = legend_title) +
  #guides(fill = guide_legend(title = legend_title)) +
  scale_shape(guide=FALSE) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ylim) +
  #scale_fill_discrete(name = "metric") +
  #scale_shape_discrete()+
#scale_fill_manual(values = c("#d8b365", "#f5f5f5", "#5ab4ac"))+
  theme_bw() + theme_classic2() +
  theme(axis.text.x = element_text(angle = 30, vjust = 1, hjust=1)) +
    theme(aspect.ratio=4/6) +
  theme(legend.position = "none")

#ggsave(save_fname, width = w, height = h)
g
```








```{r barplot interaction}
library(gghalves)

# parameters __________________________________________________________________
int_unitwise <- meanSummary(
        average_fisherz,
        c("class", "func", "metric_ordered"), "corr_z"
    )

int_groupwise <- summarySEwithin(
        data = int_unitwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("func", "metric_ordered"), # iv
        idvar = "class"
    )

subjectwise = int_unitwise
subjectwise$metric_ordered <- factor(subjectwise$metric_ordered, levels = c("mean_cca_corr", "mean_sq_cca_corr", "pwcca", "cka", "procrustes"))
subjectwise$varint <- as.factor(paste(subjectwise$metric_ordered, subjectwise$func))
subjectwise$varint <- factor(subjectwise$varint, 
                             levels = c("mean_cca_corr ablation_impact", "mean_sq_cca_corr ablation_impact", "pwcca ablation_impact", "cka ablation_impact", "procrustes ablation_impact", 
                                        "mean_cca_corr decoding_accuracy_delta", "mean_sq_cca_corr decoding_accuracy_delta", "pwcca decoding_accuracy_delta", "cka decoding_accuracy_delta", "procrustes decoding_accuracy_delta" ))
groupwise = int_groupwise
iv1 = "func"
iv2 = "metric_ordered" 
sub_mean = "mean_per_sub" 
group_mean = "mean_per_sub_norm_mean" 
se = "se" ; subject = "class"
ggtitle = paste0(model," :: interaction of functionality and metric" )

legend_title = "metric"
xlab = "metric"
ylab = "correlation between \nmetric and functionality"
w = 5
h = 10
ylim = c(-0.5,1)
dv_keyword = "correlation"
# int_color = c("#0F0F0F","#000000","#000000",
#   "#494949","#3F0005","#00003F",
#   "#838383","#7D000B","#00007D",
#   "#BDBDBD","#BC0010","#0000BC",
#   "#F7F7F7","#FA0015","#0000FA"
# )
int_color = c(
  "#000000",
   "#3F0005",
   "#7D000B",
   "#BC0010",
   "#FA0015",
   "#000000",
   "#00003F",
   "#00007D",
   "#0000BC",
   "#0000FA"
)
  #   "#000000",
  # "#00003F",
  # "#00007D",
  # "#0000BC",
  # "#0000FA"
bw_color = c("#0F0F0F", "#494949", "#838383", "#BDBDBD", "#F7F7F7")
  # decoding
g <- ggplot(data = subjectwise,
            aes(y = .data[[sub_mean]],
                x = .data[[iv1]],
                fill =varint,#.data[[iv2]],# varint, #.data[[iv2]],
                width=.9)) +
  coord_cartesian(ylim = ylim, expand = TRUE) +
  geom_flat_violin(
    aes(fill = varint),#.data[[iv2]]),
    position = position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = 0,
    colour = NA
  ) +

  geom_point(
    data = subjectwise,
    aes(
      x = .data[[iv1]],
      y = .data[[sub_mean]],
      #color = interaction(.data[[iv2]],.data[[iv1]])
      color = varint# .data[[iv2]]
    ),
    position = position_jitterdodge(), #position_jitter(width = .05),
    size = 1,
    alpha = 0.8,
    shape = 20, 
    show.legend=FALSE
  ) +

  geom_half_boxplot(
    data = subjectwise,
    aes(x = .data[[iv1]],
        y = .data[[sub_mean]],
        fill = varint),#interaction(metric_ordered,func )),
        #fill = .data[[iv2]]),
      
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .8,
    #nudge = 0.2,
    colour = "black",
    #dodge = TRUE,
    # staplelwd = 0,
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE,
    errorbar.draw = FALSE,
    center = TRUE,
    show.legend=FALSE
  ) +

  # legend stuff __________________________________________________________________________________ # nolint
  #expand_limits(x = 3.25) +

  scale_fill_manual(values = int_color, name = "metric", guide = "none") +
  scale_color_manual( values = int_color, name = "metric", guide = "none") +
  #                     name = "metric", 
  #                     breaks = c("mean_cca_corr", "mean_sq_cca_corr", "pwcca", "cka", "procrustes", ),
  #                     values = c("mean_cca_corr" = "#0F0F0F", 
  #                                "mean_sq_cca_corr" = "#494949", 
  #                                "pwcca" = "#838383", 
  #                                "cka" = "#BDBDBD", 
  #                                "procrustes" = "#F7F7F7"), 
  #                     guide = "none") +
  #scale_fill_discrete(name = "metric") +
    guides(fill = "none") +
  guides(color = "none") +
  guides(fill = guide_legend(title = legend_title)) +
  ggtitle(ggtitle) +
  # coord_flip() + #vertical vs horizontal
  xlab(xlab) +
  ylab(ylab) +
    scale_x_discrete(
    labels = c(
      "ablation_impact" = "causal deficit",
      "decoding_accuracy_delta" = "non-causal decoding"
    )
  ) +
  guides(fill =guide_legend(override.aes = list(shape = 20, size = .5))) + 
  #guides(color = guide_legend(override.aes = list(shape = 20, size = 1, alpha = 1))) +
  #guides(shape = guide_legend(override.aes = list(colour = "pink")))
  #scale_fill_manual(values = c("#d8b365", "#f5f5f5", "#5ab4ac","#f5f5f5", "#5ab4ac", "#5ab4ac", "#5ab4ac", "#5ab4ac", "#5ab4ac", "#5ab4ac"))+
  theme_bw() + theme_classic2() +
  #theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    theme(aspect.ratio=4/6) 
# + legend("bottomleft", legend = c("mean_cca_corr", "m", "cca", "cka", "procrustes"),
#     col = bw_color, bty = "n", pch=20 , pt.cex = 3, cex = 1, horiz = FALSE, inset = c(0.03, 0.1))
g 
```
```{r}
effect size
https://stats.stackexchange.com/questions/257985/how-can-i-derive-effect-sizes-in-lme4-and-describe-the-magnitude-of-fixed-effect
```


```{r}
library(gghalves)
# barplot interaction
#alexnet_naomit <- na.omit(alexnet_corr) 
#layerwise_alex <- meanSummary(alexnet_naomit, c("layer"), "z_fisher")

# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
x = "metric"
y = "mean_per_sub_norm_mean"
violin_alpha = 0.3
boxplot_alpha = 1
sep_level= 4
    if (sep_level == 4) {
      position_nudge_vector <- c(-0.2, 0,0.2)
    } else if (sep_level == 3) {
      position_nudge_vector <- c(-0.15, 0,0.15)
    } else if (sep_level == 2) {
      position_nudge_vector <- c(-0.15,0,0)
    } else if (sep_level == 1) {
      position_nudge_vector <- c(-0.08,0,0)
    } else if (sep_level == 0) {
      position_nudge_vector <- c(0,0,0)
    }
g <- ggplot(
  data = groupwise,
  aes(x = metric,
      y = mean_per_sub_norm_mean, 

           )  ) +    
  geom_point(
    data = groupwise,
    aes(
      #shape = as.character(rating_type_key),
      x =metric,
      y = mean_per_sub_norm_mean,
      ),
    #position = position_jitter(width = .05),
    size = 2
    ) +
geom_half_violin(data = groupwise,
                       aes(x = metric, y = mean_per_sub_norm_mean), side = 'r',
                       position = position_nudge(x = position_nudge_vector[3]), alpha = violin_alpha) +

        # geom_half_violin(data = groupwise,
        #                aes(x = functionality, y = mean_per_sub_norm_mean), side = 'r',
        #                position = position_nudge(x = position_nudge_vector[3]), alpha = violin_alpha) +
      geom_half_boxplot(data = groupwise,
                        aes(x = metric, y = mean_per_sub_norm_mean),
                        position = position_nudge(x = position_nudge_vector[1]),
                        side = 'r', outlier.shape = NA, center = TRUE,
                        errorbar.draw = FALSE, width = 0.2, alpha = boxplot_alpha, color = 'black') +
  scale_shape_manual(values=c(16, 21))+
geom_line()+
geom_errorbar(
  data = groupwise,
  aes(
    x = as.numeric(metric),
    y = mean_per_sub_norm_mean,
    #color = class,
    #colour = cue_ordered,
    ymin = mean_per_sub_norm_mean - se,
    ymax = mean_per_sub_norm_mean + se
    ), width = .1, size = 0.5
  ) +
          geom_point(
            data = classwise,
            aes(
                x = metric ,
                y = mean_per_sub,
                #color = functionality
            ),
            position = position_jitter(width = .05),
            size = 3, alpha = 0.8, shape = 20
        ) +
geom_hline(yintercept = 0) +
        geom_line(
            data = classwise,
            aes(
                #group = class,
                y = mean_per_sub,
                x = metric,
                #fill = functionality
            ),
            #linetype = 3,
              alpha = .3, width = .1
        ) +
 # scale_color_manual(values = c("high cue" = "red", 
                               # "low cue" = "blue")) +
  #xlab("layers") +
  ylab("correlation (fisher z)") +
  #ylim(0,100) +
  theme_bw() 
g 
```



# Main statistical test Question 01 :: Is this correlation significantly different from the null, i.e. 0? 
Using the fisher z transfor, we test whether tthe correlation coefficients are significantly different from 0, while modeling random intercepts in class and layers (allowing for class and layers to have different "mean" coefficients).
```{r}
main_dir <- dirname(getwd())
for (model in c('alexnet', 'mobilenet')) {
  analysis_dir <- file.path(main_dir, 'results', model, as.character(Sys.Date()))
  dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
  statsummary_fname <- file.path(
            analysis_dir,
            paste('statsummary_model-', model,
                '_', as.character(Sys.Date()), '.txt',
                sep = ""
            )
        )
  if (file.exists(statsummary_fname)) {
      file.remove(statsummary_fname)
  }

  statsummary <- ""
  for (dv in c('ablation_impact_X_cka', 
               'ablation_impact_X_decoding_accuracy_delta',
               'ablation_impact_X_mean_cca_corr', 
               'ablation_impact_X_mean_sq_cca_corr',
               'ablation_impact_X_procrustes', 
               'ablation_impact_X_pwcca',
               'decoding_accuracy_delta_X_cka',
               'decoding_accuracy_delta_X_mean_cca_corr',
               'decoding_accuracy_delta_X_mean_sq_cca_corr',
               'decoding_accuracy_delta_X_procrustes', 
               'decoding_accuracy_delta_X_pwcca')) {
    # load data per metric
    if (model == "alexnet") {
      data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
    } else if (model == "mobilenet") {
      data_fname <- file.path(main_dir, 'data', model, paste0(dv, '-mobilenet.csv'))
      }
  
    df <- read.csv(data_fname)
    df$fisherZ <- DescTools::FisherZ(df$correlation)
    model_cor <- lmer(fisherZ ~ 1 + (1|class) + (1|layer) , data = df)
    model_savefname <- file.path(
            analysis_dir,
            paste('lmer_model-', model,
                '_dv-', dv,
                '_', as.character(Sys.Date()), '.txt',
                sep = ""
            )
        )
  if (file.exists(model_savefname)) {
      file.remove(model_savefname)
  }
    sink(file = model_savefname)
    s <- summary(model_cor)
    capture.output(s, file = model_savefname)
    stats <- paste0('b = ',round(summary(model_cor)$coefficients[1], digits = 3), ', ',
          't(', round(summary(model_cor)$coefficients[3], digits = 2), ') = ',
          round(summary(model_cor)$coefficients[4], digits = 3),', ',
          'p = ',round(summary(model_cor)$coefficients[5],digits = 4))
    print(stats)
    sink(file = NULL)
    
    statsummary <- paste0(statsummary, '\n', '* metric: ', dv, '  >>>   stats: ', stats, '\n')
  }
  sink(file = statsummary_fname)
  # print(cat(statsummary))
  capture.output(cat(statsummary), file = statsummary_fname)
  sink(file = NULL)


}
```

# filename
# ablation_impact X cka

```{r load data}

data_fname = file.path(main_dir, 'data', model, paste0('ablation_impact_X_cka', '.csv'))
alexnet = read.csv(data_fname)
```
arise(cor = cor(decoding_accuracy_delta,ablation_impact))

```{r fisher z transform}
# fisher z transform
alexnet$fisherZ = DescTools::FisherZ(alexnet$correlation)

```


```{r}
model_cor = lmer(fisherZ ~ 1 + (1|class) + (1|layer) , data = alexnet)
model_savefname <- file.path(
        analysis_dir,
        paste('lmer_model-', model,
            '_dv-', dv,
            '_', as.character(Sys.Date()), '.txt',
            sep = ""
        )
    )
sink(file = model_savefname)
summary(model_cor)
paste0('b = ',round(summary(model_cor)$coefficients[1], digits = 3), ', ',
      't(', round(summary(model_cor)$coefficients[3], digits = 2), ') = ',
      round(summary(model_cor)$coefficients[4], digits = 3),', ',
      'p = ',round(summary(model_cor)$coefficients[5],digits = 4))
sink(file = NULL)

```


# covert estimate fisherz to r
```{r}
FisherZInv(0.19015)

```



