---
title: "iclr_corr"
author: "Anonymous"
date: '2024-01-21'
output:
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---

""" This notebook examines whether the correlation coefficients between
two metrics are statistically significant or not.

Factors: \* functionality: 1) ablation impact 2) decoding accuracy \*
metrics: 1) cka 2) mean_cca-Corr 3) mean_sq_cca_corr 4) procrustes 5)
pwcca

-   linear model of correlation coefficient (different from 0), modeling
    random intercepts for class and layer
-   I use fisher z to transform these correlation coefficients into Z
    vlaues (normal distribution)
-   From that, we get the t-estimate, testing whether this is
    significant
-   Afterward, I plan to convert the B0 estimate back into an r value,
    which is interpretable.

""" \* [ ] load data \* [ ] calculate correlation \* [ ] fisher z
transform \* [ ] model mean cor value for class layer unit

```{r load libraries, include=FALSE}
library(psych)
library(car)
#library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)
library(dplyr)
library(correlation)
library(ggplot2)
library(rmarkdown)
library(readr)
library(yaml)
library(tidyverse)
library(GGally)
library(DescTools)
library(gghalves)
library(ggpubr)
library(extrafont)
library(gridExtra)
library(patchwork)
library(emmeans)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
main_dir <- dirname(getwd())
file.sources = list.files(file.path(main_dir, 'utils'),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

```{r figure save parameters, message=FALSE, warning=FALSE}
# font_import(pattern = "DejaVu", prompt = FALSE)
# myFont <- "DejaVu Sans Mono"
w = 3
h = 1.8
units = c("in")
dpi = 600
scale = 2.5
```

```{r concatenate dataframe}


main_dir <- dirname(getwd())
model = 'alexnet_downstream'
concat_df = data.frame()
  for (dv in c('alexnet_downstream_network_delta_X_cka_x', 
               'alexnet_downstream_network_delta_X_mean_cca', 
               'alexnet_downstream_network_delta_X_mean_sq_cca',
               'alexnet_downstream_network_delta_X_procrustes_x', 
               'alexnet_downstream_network_delta_X_pwcca',
               'alexnet_linear_decoding_delta_X_cka_x',
               'alexnet_linear_decoding_delta_X_mean_cca',
               'alexnet_linear_decoding_delta_X_mean_sq_cca',
               'alexnet_linear_decoding_delta_X_procrustes_x', 
               'alexnet_linear_decoding_delta_X_pwcca')) {
  if (model == "alexnet_downstream") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
  } else if (model == "mobilenet") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
  } else if (model == "vit") {
    data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
  }
df <- read.csv(data_fname)
newdv <- sub(paste0("^", model, "_"), "", dv)
df$functionality <- strsplit(newdv, '_X_')[[1]][1]
df$metric <- strsplit(newdv, '_X_')[[1]][2]
concat_df <- rbind(concat_df, df)
}
```

```{r reverse code and contrast code}
# reverse correlation coefficient ______________________________________________
concat_df = concat_df %>% mutate(corr_transform = ifelse(metric == "mean_cca_corr" | metric == "mean_sq_cca_corr", -1 * correlation, correlation))

# drop na
concat_df <- na.omit(concat_df, cols = "correlation")

# harmonize "metric" factor (across datasets) __________________________________
concat_df$metric <- factor(concat_df$metric)
levels(concat_df$metric) <- gsub("_x", "", levels(concat_df$metric))
# levels(average_fisherz$metric)[levels(average_fisherz$metric) == "cka"] <- "mean_cca_corr"
levels(concat_df$metric)[levels(concat_df$metric) == "mean_cca"] <- "mean_cca_corr"
levels(concat_df$metric)[levels(concat_df$metric) == "mean_sq_cca"] <- "mean_sq_cca_corr"

# harmonize "func" factor (across datasets) ____________________________________
concat_df$func <- factor(concat_df$functionality)
levels(concat_df$func)[levels(concat_df$func) == "alexnet_linear_decoding_delta"] <- "decoding_accuracy_delta"
levels(concat_df$func)[levels(concat_df$func) == "network_delta"] <- "ablation_impact"
concat_df$func_con[concat_df$func == "ablation_impact"] <- -0.5
concat_df$func_con[concat_df$func == "decoding_accuracy_delta"] <- 0.5

concat_df$metric_ordered <- factor(concat_df$metric,
                                   levels=c("mean_cca_corr","mean_sq_cca_corr","pwcca","cka","procrustes"))
concat_df$metric_con  = factor(concat_df$metric_ordered)
contrasts(concat_df$metric_con) = contr.helmert(5)
```

## Let's first plot the data

We'll check the correlation distribution per class

```{r}
# Load necessary libraries
library(ggplot2)
library(dplyr)

# # Example data
# set.seed(123)
# df <- data.frame(
#   num_var = rnorm(100),
#   another_num_var = rnorm(100),
#   factor_var = factor(sample(c("A", "B", "C"), 100, replace = TRUE))
# )

# Calculate correlations per factor
correlations <- concat_df %>%
  group_by(class)
  # summarize(correlation = cor(num_var, another_num_var, use = "complete.obs"))

# Plotting the histogram
# ggplot(correlations, aes(x = correlation, group = class)) +
#   geom_histogram(bins = 10, fill = "blue", color = "black") +
#   xlab("Correlation") +
#   ylab("Frequency") +
#   ggtitle("Histogram of Correlations per Factor")

# Load the ggplot2 library
library(ggplot2)

# Assuming your dataframe is named 'df', 
# with a column 'correlation' for the correlation values,
# and a column 'class' for the class information

# Plotting the histogram with facetting by class
# ggplot(concat_df, aes(x = correlation)) +
#   geom_histogram(bins = 10, fill = "blue", color = "black") +
#   facet_wrap(~ class) + # Facet by class
#   xlab("Correlation") +
#   ylab("Frequency") +
#   ggtitle("Histogram of Correlations per Class")



ggplot(concat_df, aes(x = correlation)) +
  geom_histogram(bins = 50, fill = "blue", color = "black") +
  facet_grid(class ~ func) + # Facet by two variables
  xlab("Correlation") +
  ylab("Frequency") +
  ggtitle("Histogram of Correlations")

```

## Summary statistics for the model

Here, we average correlation values as a function of functionality X
metric per class In other words, we're averaging over the layers

```{r fisher Z along layer}
# fisher z transform and create summary statistics _____________________________
concat_df$fisherz = DescTools::FisherZ(concat_df$corr_transform)
average_fisherz <- meanSummary(concat_df,
                         c("class", "func", "metric"), "fisherz")
average_fisherz$fisherz <- average_fisherz$mean_per_sub
# average_fisherz$corr_z = DescTools::FisherZInv(average_fisherz$fisherz)
```

```{r contrast code}
# create contrast codes ________________________________________________________
average_fisherz$func_con[average_fisherz$func == "ablation_impact"] <- -0.5
average_fisherz$func_con[average_fisherz$func == "decoding_accuracy_delta"] <- 0.5

average_fisherz$func  = factor(average_fisherz$func)

# need to convert metric names append with x ___________________________________
# unique(average_fisherz$metric)
# [1] "cka_x"        "mean_cca"     "mean_sq_cca"  "procrustes_x" "pwcca" 
# average_fisherz$metric <- factor(average_fisherz$metric)
# levels(average_fisherz$metric) <- gsub("_x", "", levels(average_fisherz$metric))
# levels(average_fisherz$metric)[levels(average_fisherz$metric) == "cka"] <- "mean_cca_corr"
# levels(average_fisherz$metric)[levels(average_fisherz$metric) == "mean_cca"] <- "mean_cca_corr"
# levels(average_fisherz$metric)[levels(average_fisherz$metric) == "mean_sq_cca"] <- "mean_sq_cca_corr"
average_fisherz$metric_ordered <- factor(average_fisherz$metric, 
                                   levels=c("mean_cca_corr","mean_sq_cca_corr","pwcca","cka","procrustes"))
average_fisherz$metric_con  = factor(average_fisherz$metric_ordered)
contrasts(average_fisherz$metric_con) = contr.helmert(5)

```

## linear model

```{r}

model.tst <- lmer(fisherz ~ func_con * metric_con + (1 |class), data = concat_df )
summary(model.tst)
```

```{r model with fisherz inverse transformed metrics}
full = lmer(fisherz ~ func_con * metric_con + (1|class), data = average_fisherz)
summary(full)
```

## Omnibus results

```{r}
Anova(full, type = "III", test.statistic = "F")
```

# simple effects

```{r}
library(emmeans)
# emmeans(full, list(pairwise ~ metric_con* func_con), adjust = "tukey")
library(emmeans)
emm1 = emmeans(full, specs =  ~ metric_con* func_con)

cka_mean = c(0,0,0,1/2,0, 0,0,0,1/2,0)
procrustes_mean = c(0,0,0,0,1/2, 0,0,0,0,1/2)

cka_mean_causal = c(0,0,0,1/2,0, 0,0,0,0,0)
procrustes_mean_causal = c(0,0,0,0,1/2, 0,0,0,0,0)

cka_mean_noncausal = c(0,0,0,0,0, 0,0,0,1/2,0)
procrustes_mean_noncausal = c(0,0,0,0,0, 0,0,0,0,1/2)

cca_mean = c(1/6, 1/6, 1/6, 0, 0, 1/6, 1/6, 1/6, 0, 0)
cka_pro = c(0,0,0,1/4,1/4, 0,0,0,1/4,1/4)

cca_mean_causal = c(1/3, 1/3, 1/3, 0, 0,0,0,0,0,0)
cka_pro_causal = c(0,0,0,1/2,1/2,0,0,0,0,0)

cca_mean_noncausal = c(0,0,0,0,0,1/3, 1/3, 1/3, 0, 0)
cka_pro_noncausal = c(0,0,0,0,0,  0,0,0,1/2,1/2)

int = c(1,1,1,1,1,-1,-1,-1,-1,-1)
contrast(emm1, method = list("cka/procrustes vs. mean_cca/mean_sq/pwcca on average" = cka_pro - cca_mean, 
                             "procrustes vs. cka on average" = procrustes_mean - cka_mean,
                             "procrustes vs. cka causal" = procrustes_mean_causal - cka_mean_causal,
                             "procrustes vs. cka noncausal" = procrustes_mean_noncausal - cka_mean_noncausal,
                             "within causal, cka/procrustes vs. mean_cca/mean_sq/pwcca" =  cka_pro_causal - cca_mean_causal,
                             "within noncausal, cka/procrustes vs. mean_cca/mean_sq/pwcca" = cka_pro_noncausal - cca_mean_noncausal,
                             "interaction, cka/procrustex vs. cca vs. functionality" = (cka_pro_causal - cca_mean_causal) - (cka_pro_noncausal - cca_mean_noncausal) ) )

```

## plot 1: functionality

```{r barplot functionality}
# parameters __________________________________________________________________
model_keyword = "mobilenet"
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "func"
ylim = c(-.25, .8)
se = "se"
subject = "class"
ggtitle = paste0(model_keyword,
                 " :: Functionality, averaged across layers and classes")
legend_title = "Functionality"
xlab = "Functionality "
ylab = "Correlation between \nmetric and functionality"

dv_keyword = "corr"

classwise <- meanSummary(average_fisherz,
                         c(subject, iv), "corr_z")
groupwise <- summarySEwithin(
  data = classwise,
  measurevar = "mean_per_sub",
  withinvars = c(iv),
  idvar = subject
)

subjectwise = classwise

if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#D73027", "#4575B4")
}

# ggplot ______________________________________________________________________
p1 <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',
    adjust = 1.5,
    trim = FALSE,
    alpha = .3,
    colour = NA
  ) +
    geom_line(data = subjectwise,
    aes(
      group = .data[[subject]],
      x = as.numeric(.data[[iv]]) - .15,
      y = .data[[subjectwise_mean]],
      fill = factor(.data[[iv]])
      ),
    linetype = "solid",
    color = "grey",
    alpha = .3) +

  geom_point(
    aes(
      x = as.numeric(.data[[iv]]) - .15,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .1,
    colour = "black",
    errorbar.draw = FALSE
  ) +
  
  # legend stuff ________________________________________________________
  
  guides(color = "none") +
  guides(fill = guide_legend(title = legend_title)) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  scale_x_discrete(
    labels = c(
      "network_delta" = "Causal deficit",
      "alexnet_linear_decoding_delta" = "Non-causal Decoding"
      # "ablation_impact" = "Causal deficit",
      # "decoding_accuracy_delta" = "Non-causal Decoding"
    )
  ) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ylim )+
  
  theme_bw() + theme_classic2() +
  theme(aspect.ratio = 6 / 10) 
  # theme(legend.position = "none",
  #       text = element_text(family = "DejaVu Sans"), 
  #       plot.title = element_text(size=12))

save_fname <-
  file.path(main_dir, 'figure', model,
            paste0(model, '01_iv-', iv, '_dv-', dv_keyword, '.png'))

# ggsave(
#   save_fname,
#   width = w,
#   unit = "in",
#   dpi = 600,
#   scale = 2.5
# )
p1
```

## plot 2: metric

```{r barplot metric}
# parameters __________________________________________________________________
metric_classwise <- meanSummary(
        average_fisherz,
        c("class","metric_con"), "corr_z"
    )

metric_groupwise <- summarySEwithin(
        data = metric_classwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c( "metric_con"), # iv
        idvar = "class"
    )

subjectwise = metric_classwise
groupwise = metric_groupwise
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "metric_con"
ylim = c(-0.1, .5)
se = "se"
subject = "class"
ggtitle = paste0(model_keyword, " :: Metrics, averaged across layers and classes")
legend_title = "metric"
xlab = "Metric"
ylab = "Correlation between \nmetric and functionality"
iv_keyword = "metric"
dv_keyword = "corr"

if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#464655", "#898983","#B6B6C1", "#CECEE0", "#DEDEEF")
} else {
  color <- c( "#000000","#2D0040", "#5A0080","#8600BF","#B300FF")
}

# ggplot ______________________________________________________________________
p2 <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',#position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = TRUE,
    alpha = .3,
    colour = NA
  ) +
  
  geom_point(
    aes(
      x = as.numeric(factor(.data[[iv]])) - .15 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    #shape = 20
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .2,
    colour = "black",
    # staplelwd = 0,
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE, 
    errorbar.draw = FALSE
  ) +
  
  
  # legend stuff ________________________________________________________ # nolint

  guides(fill = guide_legend(override.aes = list(shape = 20, size = 1, alpha = 1))) +
           theme(legend.title = legend_title) +
  scale_shape(guide=FALSE) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ylim) +
  theme_bw() + theme_classic2() +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  )) +
  theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "bottom",#"none",
        # text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=12))
save_fname <-
  file.path(main_dir, 'figure', model,
            paste0(model, '02_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))
ggsave(
  save_fname,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5
)

p2
```

## plot 3: interaction

```{r barplot interaction}
library(gghalves)

# parameters __________________________________________________________________
int_unitwise <- meanSummary(
        average_fisherz,
        c("class", "func", "metric_ordered"), "corr_z"
    )

int_groupwise <- summarySEwithin(
        data = int_unitwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("func", "metric_ordered"), # iv
        idvar = "class"
    )

subjectwise = int_unitwise
subjectwise$metric_ordered <- factor(subjectwise$metric_ordered, levels = c("mean_cca_corr", "mean_sq_cca_corr", "pwcca", "cka", "procrustes"))
subjectwise$varint <- as.factor(paste(subjectwise$metric_ordered, subjectwise$func))
subjectwise$varint <- factor(subjectwise$varint, 
                             levels = c("mean_cca_corr ablation_impact", "mean_sq_cca_corr ablation_impact", "pwcca ablation_impact", "cka ablation_impact", "procrustes ablation_impact", 
                                        "mean_cca_corr decoding_accuracy_delta", "mean_sq_cca_corr decoding_accuracy_delta", "pwcca decoding_accuracy_delta", "cka decoding_accuracy_delta", "procrustes decoding_accuracy_delta" ))
groupwise = int_groupwise
iv1 = "func"
iv2 = "metric_ordered" 
sub_mean = "mean_per_sub" 
group_mean = "mean_per_sub_norm_mean" 
se = "se" ; subject = "class"
ggtitle = paste0(model_keyword," :: Interaction of functionality and metric" )

legend_title = "Metric"
xlab = "Functionality"
ylab = "Correlation between \nmetric and functionality"
iv_keyword = "int"
dv_keyword = "corr"

int_color = c(
  "#000000",   "#3F0005",   "#7D000B",   "#BC0010",   "#FA0015",
   "#000000",   "#00003F",   "#00007D",   "#0000BC",   "#0000FA"
)

bw_color = c("#0F0F0F", "#494949", "#838383", "#BDBDBD", "#F7F7F7")
  # decoding
p3 <- ggplot(data = subjectwise,
            aes(y = .data[[sub_mean]],
                x = .data[[iv1]],
                fill =varint,#.data[[iv2]],# varint, #.data[[iv2]],
                width=.9)) +
  geom_flat_violin(
    aes(fill = varint),#.data[[iv2]]),
    position = position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = 0,
    colour = NA
  ) +

  geom_point(
    data = subjectwise,
    aes(
      x = .data[[iv1]],
      y = .data[[sub_mean]],
      color = varint# .data[[iv2]]
    ),
    position = position_jitterdodge(), #position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    shape = 20, 
    show.legend=FALSE
  ) +

  geom_half_boxplot(
    data = subjectwise,
    aes(x = .data[[iv1]],
        y = .data[[sub_mean]],
        fill = varint),#interaction(metric_ordered,func )),

    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .8,
    colour = "black",
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE,
    errorbar.draw = FALSE,
    center = TRUE,
    show.legend=TRUE
  ) +

  # legend stuff __________________________________________________________________________________ # nolint

  scale_fill_manual(values = int_color, name = "metric", guide = "none") +
  scale_color_manual( values = int_color, name = "metric", guide = "none") +

    guides(fill = "none") +
  guides(color = "none") +

  ggtitle(ggtitle) +

  xlab(xlab) +
  ylab(ylab) +
    scale_x_discrete(
    labels = c(
      "ablation_impact" = "Causal deficit",
      "decoding_accuracy_delta" = "Non-causal decoding"
    )
  ) +


  theme_bw() + theme_classic2() +
  
    #theme(aspect.ratio=4/6) 
theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "bottom", #"none",
        # text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=14))


print(p3)
save_fname <-
  file.path(main_dir, 'figure', model,
            paste0(model, '03_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))


ggsave(
  save_fname,
  plot = p3,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5)
```

# contrast code CKA/Procrustes vs CCA

```{r}
average_fisherz$func_con[average_fisherz$functionality == "ablation_impact"] <- -0.5
average_fisherz$func_con[average_fisherz$functionality == "decoding_accuracy_delta"] <- 0.5


average_fisherz$metric_cca[average_fisherz$metric == "cka"] <- 0.5
average_fisherz$metric_cca[average_fisherz$metric == "procrustes"] <- 0.5
average_fisherz$metric_cca[average_fisherz$metric == "mean_cca_corr"] <- -0.5
average_fisherz$metric_cca[average_fisherz$metric == "mean_sq_cca_corr"] <- -0.5
average_fisherz$metric_cca[average_fisherz$metric == "pwcca"] <- -0.5

average_fisherz$func  = factor(average_fisherz$functionality)
model.cca = lmer(corr_z ~ func_con * metric_cca + (1|class)  , data = average_fisherz)
summary(model.cca)
```

```{r}
library(emmeans)

```

```{r}
Anova(full, type = "III", test.statistic = "F")
```

```{r}
library(emmeans)
emm1 = emmeans(full, specs =  ~ metric_con* func_con)

om_1 = c(-1, -1, -1, -1, 4, 0,0,0,0,0)
om_2 = c(-1, -1, -1, 3, 0, 0,0,0,0,0)
om_3 = c(-1, -1, 2, 0, 0, 0,0,0,0,0)
om_4 = c(-1, 1, 0,0,0, 0,0,0,0,0)

tom_1 = c(-1, -1, -1, -1, 4,-1, -1, -1, -1, 4)
tom_2 = c(-1, -1, -1, 3, 0,-1, -1, -1, 3, 0)
tom_3 = c(-1, -1, 2, 0, 0,-1, -1, 2, 0, 0)
tom_4 = c(-1, 1, 0,0,0,-1, 1, 0,0,0)

cka_mean = c(0,0,0,1/2,0, 0,0,0,1/2,0)
procrustes_mean = c(0,0,0,0,1/2, 0,0,0,0,1/2)

cka_mean_causal = c(0,0,0,1/2,0, 0,0,0,0,0)
procrustes_mean_causal = c(0,0,0,0,1/2, 0,0,0,0,0)

cka_mean_noncausal = c(0,0,0,0,0, 0,0,0,1/2,0)
procrustes_mean_noncausal = c(0,0,0,0,0, 0,0,0,0,1/2)

cca_mean = c(1/6, 1/6, 1/6, 0, 0, 1/6, 1/6, 1/6, 0, 0)
cka_pro = c(0,0,0,1/4,1/4, 0,0,0,1/4,1/4)

cca_mean_causal = c(1/3, 1/3, 1/3, 0, 0,0,0,0,0,0)
cka_pro_causal = c(0,0,0,1/2,1/2,0,0,0,0,0)

cca_mean_noncausal = c(0,0,0,0,0,1/3, 1/3, 1/3, 0, 0)
cka_pro_noncausal = c(0,0,0,0,0,  0,0,0,1/2,1/2)

int = c(1,1,1,1,1,-1,-1,-1,-1,-1)
contrast(emm1, method = list("cka/procrustes vs. mean_cca/mean_sq/pwcca on average" = cka_pro - cca_mean, 
                             "procrustes vs. cka on average" = procrustes_mean - cka_mean,
                             "procrustes vs. cka causal" = procrustes_mean_causal - cka_mean_causal,
                             "procrustes vs. cka noncausal" = procrustes_mean_noncausal - cka_mean_noncausal,
                             "within causal, cka/procrustes vs. mean_cca/mean_sq/pwcca" =  cka_pro_causal - cca_mean_causal,
                             "within noncausal, cka/procrustes vs. mean_cca/mean_sq/pwcca" = cka_pro_noncausal - cca_mean_noncausal,
                             "omb_causa" = om_1 - om_2 - om_3 - om_4, 
                             "omb_test" = (tom_1+tom_2+tom_3+tom_4)/4,
                              "interaction, cka/procrustex vs. cca vs. functionality" = (cka_pro_causal - cca_mean_causal) - (cka_pro_noncausal - cca_mean_noncausal)
         ))
```

```{r}
(0.2640)/sqrt(0.0008049 +0.0008930 ) # d: mobilnet, cka/procrustes vs. mean_cca/mean_sq/pwcca on average
(0.0185)/sqrt(0.0008049 +0.0008930 ) # d: procrustes vs. cka on average
(0.0177)/sqrt(0.0008049 +0.0008930 ) # d: procrustes vs. cka causal   
(0.0193)/sqrt(0.0008049 +0.0008930 ) # d: procrustes vs. cka causal  
```

```{r}
design_result <- ANOVA_design(design = "2w*5w", n = 10, mu = c(0.2, 0.2, 0.2, 0.2, 0.2, 0.6, 0.6, 0.6, 0.9, 0.9),
      sd = 2, r = 0.1, labelnames = c("functionality", "network", "decoding", "metric", "mean",
      "mean_sq", "cca", "cka", "procrustes" ))
exact_result <- ANOVA_exact(design_result, alpha_level = 0.05)
```

```         
effect size
https://stats.stackexchange.com/questions/257985/how-can-i-derive-effect-sizes-in-lme4-and-describe-the-magnitude-of-fixed-effect
```

# linear plots

```{r pivot dataframe long to wide}
library(tidyverse)
# subset dataframe and convert to wide frame
subset = concat_df %>% select(X, class, layer, correlation, functionality, metric)
wide = subset %>% 
   mutate(functionality = str_c('func_', functionality)) %>%
   pivot_wider(names_from = functionality, values_from = c(correlation))

```

```{r scale correlation within layer and class}
library(ggplot2)
corr_linear = wide %>%
        group_by(layer, class) %>%
        mutate(z_causal_deficit = scale(func_network_delta),
              z_noncausal_decoding = scale(func_alexnet_linear_decoding_delta))

```

```{r scale correlation within layer and class}
# # check dataframe
# corr_linear %>%
#         group_by(layer, class, metric) %>%
#         mutate(mean_metric = scale(metric),
#               z_noncausal_decoding = scale(func_decoding_accuracy_delta))

```

```{r}
k <- ggplot(corr_linear) +
  geom_point(aes(x = z_causal_deficit,
                 y = z_noncausal_decoding,
                 color = layer)) +
  geom_smooth(aes(x = z_causal_deficit,
                  y = z_noncausal_decoding,
                  color = layer)) +
  facet_wrap( ~ class) +
  theme_bw() +
  labs(title = "bw Theme")
k 
```

```{r}
library(gghalves)
# barplot interaction
#alexnet_naomit <- na.omit(alexnet_corr) 
#layerwise_alex <- meanSummary(alexnet_naomit, c("layer"), "z_fisher")

# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
x = "metric"
y = "mean_per_sub_norm_mean"
violin_alpha = 0.3
boxplot_alpha = 1
sep_level= 4
    if (sep_level == 4) {
      position_nudge_vector <- c(-0.2, 0,0.2)
    } else if (sep_level == 3) {
      position_nudge_vector <- c(-0.15, 0,0.15)
    } else if (sep_level == 2) {
      position_nudge_vector <- c(-0.15,0,0)
    } else if (sep_level == 1) {
      position_nudge_vector <- c(-0.08,0,0)
    } else if (sep_level == 0) {
      position_nudge_vector <- c(0,0,0)
    }
g <- ggplot(
  data = groupwise,
  aes(x = metric,
      y = mean_per_sub_norm_mean, 

           )  ) +    
  geom_point(
    data = groupwise,
    aes(
      #shape = as.character(rating_type_key),
      x =metric,
      y = mean_per_sub_norm_mean,
      ),
    #position = position_jitter(width = .05),
    size = 2
    ) +
geom_half_violin(data = groupwise,
                       aes(x = metric, y = mean_per_sub_norm_mean), side = 'r',
                       position = position_nudge(x = position_nudge_vector[3]), alpha = violin_alpha) +

        # geom_half_violin(data = groupwise,
        #                aes(x = functionality, y = mean_per_sub_norm_mean), side = 'r',
        #                position = position_nudge(x = position_nudge_vector[3]), alpha = violin_alpha) +
      geom_half_boxplot(data = groupwise,
                        aes(x = metric, y = mean_per_sub_norm_mean),
                        position = position_nudge(x = position_nudge_vector[1]),
                        side = 'r', outlier.shape = NA, center = TRUE,
                        errorbar.draw = FALSE, width = 0.2, alpha = boxplot_alpha, color = 'black') +
  scale_shape_manual(values=c(16, 21))+
geom_line()+
geom_errorbar(
  data = groupwise,
  aes(
    x = as.numeric(metric),
    y = mean_per_sub_norm_mean,
    #color = class,
    #colour = cue_ordered,
    ymin = mean_per_sub_norm_mean - se,
    ymax = mean_per_sub_norm_mean + se
    ), width = .1, size = 0.5
  ) +
          geom_point(
            data = classwise,
            aes(
                x = metric ,
                y = mean_per_sub,
                #color = functionality
            ),
            position = position_jitter(width = .05),
            size = 3, alpha = 0.8, shape = 20
        ) +
geom_hline(yintercept = 0) +
        geom_line(
            data = classwise,
            aes(
                #group = class,
                y = mean_per_sub,
                x = metric,
                #fill = functionality
            ),
            #linetype = 3,
              alpha = .3, width = .1
        ) +
 # scale_color_manual(values = c("high cue" = "red", 
                               # "low cue" = "blue")) +
  #xlab("layers") +
  ylab("correlation (fisher z)") +
  #ylim(0,100) +
  theme_bw() 
g 
```

# Main statistical test Question 01 :: Is this correlation significantly different from the null, i.e. 0?

Using the fisher z transfor, we test whether tthe correlation
coefficients are significantly different from 0, while modeling random
intercepts in class and layers (allowing for class and layers to have
different "mean" coefficients).

```{r}
main_dir <- dirname(getwd())
for (model in c('alexnet', 'mobilenet')) {
  analysis_dir <- file.path(main_dir, 'results', model, as.character(Sys.Date()))
  dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
  statsummary_fname <- file.path(
            analysis_dir,
            paste('statsummary_model-', model,
                '_', as.character(Sys.Date()), '.txt',
                sep = ""
            )
        )
  if (file.exists(statsummary_fname)) {
      file.remove(statsummary_fname)
  }

  statsummary <- ""
  for (dv in c('ablation_impact_X_cka', 
               'ablation_impact_X_decoding_accuracy_delta',
               'ablation_impact_X_mean_cca_corr', 
               'ablation_impact_X_mean_sq_cca_corr',
               'ablation_impact_X_procrustes', 
               'ablation_impact_X_pwcca',
               'decoding_accuracy_delta_X_cka',
               'decoding_accuracy_delta_X_mean_cca_corr',
               'decoding_accuracy_delta_X_mean_sq_cca_corr',
               'decoding_accuracy_delta_X_procrustes', 
               'decoding_accuracy_delta_X_pwcca')) {
    # load data per metric
    if (model == "alexnet") {
      data_fname <- file.path(main_dir, 'data', model, paste0(dv, '.csv'))
    } else if (model == "mobilenet") {
      data_fname <- file.path(main_dir, 'data', model, paste0(dv, '-mobilenet.csv'))
      }
  
    df <- read.csv(data_fname)
    df$fisherZ <- DescTools::FisherZ(df$correlation)
    model_cor <- lmer(fisherZ ~ 1 + (1|class) + (1|layer) , data = df)
    model_savefname <- file.path(
            analysis_dir,
            paste('lmer_model-', model,
                '_dv-', dv,
                '_', as.character(Sys.Date()), '.txt',
                sep = ""
            )
        )
  if (file.exists(model_savefname)) {
      file.remove(model_savefname)
  }
    sink(file = model_savefname)
    s <- summary(model_cor)
    capture.output(s, file = model_savefname)
    stats <- paste0('b = ',round(summary(model_cor)$coefficients[1], digits = 3), ', ',
          't(', round(summary(model_cor)$coefficients[3], digits = 2), ') = ',
          round(summary(model_cor)$coefficients[4], digits = 3),', ',
          'p = ',round(summary(model_cor)$coefficients[5],digits = 4))
    print(stats)
    sink(file = NULL)
    
    statsummary <- paste0(statsummary, '\n', '* metric: ', dv, '  >>>   stats: ', stats, '\n')
  }
  sink(file = statsummary_fname)
  # print(cat(statsummary))
  capture.output(cat(statsummary), file = statsummary_fname)
  sink(file = NULL)


}
```

# filename

# ablation_impact X cka

```{r load data}

data_fname = file.path(main_dir, 'data', model, paste0('ablation_impact_X_cka', '.csv'))
alexnet = read.csv(data_fname)
```

arise(cor = cor(decoding_accuracy_delta,ablation_impact))

```{r fisher z transform}
# fisher z transform
alexnet$fisherZ = DescTools::FisherZ(alexnet$correlation)

```

```{r}
model_cor = lmer(fisherZ ~ 1 + (1|class) + (1|layer) , data = alexnet)
model_savefname <- file.path(
        analysis_dir,
        paste('lmer_model-', model,
            '_dv-', dv,
            '_', as.character(Sys.Date()), '.txt',
            sep = ""
        )
    )
sink(file = model_savefname)
summary(model_cor)
paste0('b = ',round(summary(model_cor)$coefficients[1], digits = 3), ', ',
      't(', round(summary(model_cor)$coefficients[3], digits = 2), ') = ',
      round(summary(model_cor)$coefficients[4], digits = 3),', ',
      'p = ',round(summary(model_cor)$coefficients[5],digits = 4))
sink(file = NULL)

```

# covert estimate fisherz to r

```{r}
FisherZInv(0.19015)

```
