---
title: "nn_corr_multilevel_fisherz_alex_revision_perlayer"
author: "Anonymous"
date: "2022-11-17"
output: html_document
---
---
title: "iclr_corr"
author: "Anonymous"
date: '2022-11-11'
output:
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---

""" This notebook examines whether the correlation coefficients between
two metrics are statistically significant or not.

Factors: \* functionality: 1) ablation impact 2) decoding accuracy \*
metrics: 1) cka 2) mean_cca-Corr 3) mean_sq_cca_corr 4) procrustes 5)
pwcca

Methods:

-   linear model of correlation coefficient (different from 0), modeling
    random intercepts for class and layer
-   I use fisher z to transform these correlation coefficients into Z
    vlaues (normal distribution)
-   From that, we get the t-estimate, testing whether this is
    significant
-   Afterward, I plan to convert the B0 estimate back into an r value,
    which is interpretable.

TODO: concatenate all .csv files make sure that the factor information
is inserted into each """ \# load data \# calculate correlation \#
fisher z transform \# model mean cor value for class layer unit

## libraries
```{r load libraries, include=FALSE}
library(psych)
library(car)
#library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)
library(dplyr)
library(correlation)
library(ggplot2)
library(rmarkdown)
library(readr)
library(yaml)
library(tidyverse)
library(GGally)
library(DescTools)
library(gghalves)
library(ggpubr)
library(extrafont)
library(gridExtra)
library(patchwork)
library(DescTools)

source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

```{r figure save parameters}
font_import(pattern = "DejaVu", prompt = FALSE)
myFont <- "DejaVu Sans Mono"
w = 3
h = 1.8
units = c("in")
dpi = 600
scale = 2.5
```


# load data
```{r}
main_dir <- dirname(dirname(getwd()))
fname <- file.path(main_dir, 'revision', 'data', 'all_50_classes_all_metrics_correlations.csv')
df <- read.csv(fname)
df$functionality = df$A
df$metric = df$B
concat_df = df
```

```{r reverse code and contrast code}
concat_df = concat_df %>% mutate(corr_transform = ifelse(metric == "mean_cca_corr" | metric == "mean_sq_cca_corr", -1 * correlation, correlation))
```

```{r fisher z transform}
N <- concat_df %>%
  group_by(class ,layer, functionality)  %>%
  mutate(fisherz = DescTools::FisherZ(corr_transform))
average_fisherz <- meanSummary(N,
                         c("class", "layer", "functionality"), "fisherz")
average_fisherz$fisherz <- average_fisherz$mean_per_sub
average_fisherz$corr_z = DescTools::FisherZInv(average_fisherz$fisherz)


# N <- concat_df %>% 
#   group_by(class )  %>%
#   mutate(fisherz = DescTools::FisherZ(corr_transform))
# average_fisherz <- meanSummary(N,
#                          c("class", "layer", "functionality", "metric"), "fisherz")
# average_fisherz$fisherz <- average_fisherz$mean_per_sub
# average_fisherz$corr_z = DescTools::FisherZInv(average_fisherz$fisherz)
```

1)  transformed mean_cca_corr mean_sq_cca_corr inverse
2)  fisher z for correlations
3)  within class/functionality/layers
4)  average

```{r contrast code}
average_fisherz$func_con[average_fisherz$functionality == "ablation_impact"] <- -0.5
average_fisherz$func_con[average_fisherz$functionality == "decoding_accuracy_delta"] <- 0.5

average_fisherz$func  = factor(average_fisherz$functionality)
average_fisherz$layer_ordered <- factor(average_fisherz$layer, 
                                   levels=c("conv_1","conv_2","conv_3","conv_4","conv_5", "dense_1", "dense_2"))
average_fisherz$layer_con  = factor(average_fisherz$layer_ordered)

contrasts(average_fisherz$layer_con) = contr.helmert(7)
```

# Multilevel modeling
```{r multilevel modeling }
full = lmer(corr_z ~ func_con * layer_con + (1|class)  , data = average_fisherz)
summary(full)
```

# pairwisee
```{r}
library(emmeans)
emmeans(full, list(pairwise ~ layer_con* func_con), adjust = "tukey")
```

```{r}
Anova(full, type = "III", test.statistic = "F")
```

```{r raincloudplots main effect of functionality}
# parameters __________________________________________________________________
model = 'alexnet'
model_keyword = "Alexnet"
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "func"
ylim = c(-.25, .8)
se = "se"
subject = "class"
ggtitle = paste0(model_keyword,
                 " :: Functionality, averaged across layers and classes")
legend_title = "Functionality"
xlab = "Functionality "
ylab = "Correlation between \nmetric and functionality"

dv_keyword = "corr"

classwise <- meanSummary(average_fisherz,
                         c(subject, iv), "corr_z")

groupwise <- summarySEwithin(
  data = classwise,
  measurevar = "mean_per_sub",
  withinvars = c(iv),
  idvar = subject
)

subjectwise = classwise
color <- c("#D73027", "#4575B4")
# if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
#   color <- c("#1B9E77", "#D95F02")
# } else {
#   color <- c("#D73027", "#4575B4")
# }

# ggplot ______________________________________________________________________
p1 <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',
    adjust = 1.5,
    trim = FALSE,
    alpha = .3,
    colour = NA
  ) +
  
  geom_line(data = subjectwise,
    aes(
      group = .data[[subject]],
      x = as.numeric(.data[[iv]]) - .15,
      y = .data[[subjectwise_mean]],
      fill = factor(.data[[iv]])
      ),
    linetype = "solid",
    color = "grey",
    alpha = .3) +

  geom_point(
    aes(
      x = as.numeric(.data[[iv]]) - .15,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .1,
    colour = "black",
    errorbar.draw = FALSE
  ) +
  
  # legend stuff ________________________________________________________
  
  guides(color = "none") +
  guides(fill = guide_legend(title = legend_title)) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  scale_x_discrete(
    labels = c(
      "ablation_impact" = "Network performance deficits",
      "decoding_accuracy_delta" = "Decoding accuracy deficits"
    )
  ) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ylim) +
  theme_bw() + theme_classic2() +
  theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=12))

save_fname <-
  file.path(main_dir,'revision',
            'results',
            'figure',
            paste0(model, '01_iv-', iv, '_dv-', dv_keyword, '.png'))
ggsave(
  save_fname,
  width = w,
  unit = "in",
  dpi = 600,
  scale = 2.5
)
p1
```

```{r raincloudplots main effect of layer}
# parameters __________________________________________________________________
metric_classwise <- meanSummary(
        average_fisherz,
        c("class","layer_con"), "corr_z"
    )

metric_groupwise <- summarySEwithin(
        data = metric_classwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c( "layer_con"), # iv
        idvar = "class"
    )

subjectwise = metric_classwise
groupwise = metric_groupwise
subjectwise_mean = "mean_per_sub"
group_mean = "mean_per_sub_norm_mean"
iv = "layer_con"
ylim = c(0, .5)
se = "se"
subject = "class"
ggtitle = paste0(model_keyword, " :: average value across metrics and functionality")
legend_title = "layer"
xlab = "Layer"
ylab = "Correlation between \nlayer and functionality"
iv_keyword = "layer"
dv_keyword = "corr"
color <- c( "#FFE74C","#EDC16A", "#DB9C88","#C976A6","#B750C3",  "#A52BE1", "#9305FF")

# ggplot ______________________________________________________________________
p2 <- ggplot(data = subjectwise,
            aes(
              y = .data[[subjectwise_mean]],
              x = factor(.data[[iv]]),
              fill = factor(.data[[iv]])
            )) +
  geom_half_violin(
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',
    adjust = 1.5,
    trim = TRUE,
    alpha = .3,
    colour = NA
  ) +
  
  geom_point(
    aes(
      x = as.numeric(factor(.data[[iv]])) - .15 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
  ) +
  
  geom_half_boxplot(
    aes(x = .data[[iv]],
        y = .data[[subjectwise_mean]],
        fill = .data[[iv]]),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .2,
    colour = "black",
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE, 
    errorbar.draw = FALSE
  ) +
  
  # legend stuff ________________________________________________________ # nolint

  guides(fill = guide_legend(override.aes = list(shape = 20, size = 1, alpha = 1))) +
           theme(legend.title = legend_title) +
  scale_shape(guide=FALSE) +
  scale_fill_manual(values = color) +
  scale_color_manual(values = color) +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ylim) +
  theme_bw() + theme_classic2() +
  theme(axis.text.x = element_text(
    angle = 30,
    vjust = 1,
    hjust = 1
  )) +
  theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=12))
save_fname <-
  file.path(main_dir,'revision',
            'results',
            'figure',
            paste0(model, '02_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))
ggsave(
  save_fname,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5
)

p2
```

```{r raincloudplots interaction}
library(gghalves)

# parameters __________________________________________________________________
average_fisherz$func = average_fisherz$functionality
int_unitwise <- meanSummary(
        average_fisherz,
        c("class", "func", "layer_ordered"), "corr_z"
    )

int_groupwise <- summarySEwithin(
        data = int_unitwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("func", "layer_ordered"), # iv
        idvar = "class"
    )

subjectwise = int_unitwise
subjectwise$layer_ordered <- factor(
  subjectwise$layer_ordered,
  levels = c("conv_1","conv_2","conv_3","conv_4","conv_5","dense_1","dense_2")
)
subjectwise$varint <-
  as.factor(paste(subjectwise$layer_ordered, subjectwise$func))
subjectwise$varint <- factor(
  subjectwise$varint,
  levels =  c(
    "conv_1 ablation_impact",
    "conv_2 ablation_impact",
    "conv_3 ablation_impact",
    "conv_4 ablation_impact",
    "conv_5 ablation_impact",
    "dense_1 ablation_impact",
    "dense_2 ablation_impact",
    "conv_1 decoding_accuracy_delta",
    "conv_2 decoding_accuracy_delta",
    "conv_3 decoding_accuracy_delta",
    "conv_4 decoding_accuracy_delta",
    "conv_5 decoding_accuracy_delta",
    "dense_1 decoding_accuracy_delta",
    "dense_2 decoding_accuracy_delta"
  )
)
groupwise = int_groupwise
iv1 = "func"
iv2 = "layer_ordered" 
sub_mean = "mean_per_sub" 
group_mean = "mean_per_sub_norm_mean" 
se = "se" ; subject = "class"
ggtitle = paste0(model_keyword," :: Interaction of functionality and layer" )

legend_title = "Layer"
xlab = "Functionality"
ylab = "Correlation between \nlayer and functionality"
iv_keyword = "int_funcXlayer"
dv_keyword = "corr"

int_color = c("#FFECC9","#FFCFA8","#FFB386","#FF9665","#FF7943","#FF5D22","#FF4000",
  "#FFECC9","#D5E8D2","#AAE4DB","#80E0E4","#55DCED","#2BD8F6","#00D4FF"
)

bw_color = c("#0F0F0F", "#494949", "#838383", "#BDBDBD", "#F7F7F7", "#BDBDBD", "#F7F7F7")
p3 <- ggplot(data = subjectwise,
            aes(y = .data[[sub_mean]],
                x = .data[[iv1]],
                fill =varint,
                width=.9)) +
  geom_flat_violin(
    aes(fill = varint),#.data[[iv2]]),
    position = position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = 0,
    colour = NA
  ) +

  geom_point(
    data = subjectwise,
    aes(
      x = .data[[iv1]],
      y = .data[[sub_mean]],
      color = varint
    ),
    position = position_jitterdodge(), 
    size = 2,
    alpha = 0.8,
    shape = 20, 
    show.legend=FALSE
  ) +

  geom_half_boxplot(
    data = subjectwise,
    aes(x = .data[[iv1]],
        y = .data[[sub_mean]],
        fill = varint),
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .8,
    colour = "black",
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE,
    errorbar.draw = FALSE,
    center = TRUE,
    show.legend=TRUE
  ) +

  # legend stuff __________________________________________________________________________________ # nolint

  scale_fill_manual(values = int_color, name = "metric", guide = "none") +
  scale_color_manual( values = int_color, name = "metric", guide = "none") +

  guides(fill = "none") +
  guides(color = "none") +
  ggtitle(ggtitle) +
  xlab(xlab) +
  ylab(ylab) +
    scale_x_discrete(
    labels = c(
      "ablation_impact" = "Network performance deficits",
      "decoding_accuracy_delta" = "Decoding accuracy deficits"
    )
  ) +

  theme_bw() + theme_classic2() +
    #theme(aspect.ratio=4/6) 
theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=14))


p3
save_fname <-
  file.path(main_dir,'revision',
            'results',
            'figure',
            paste0(model, '03_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))


ggsave(
  save_fname,
  plot = p3,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5)
```

```{r DEBUG}
library(gghalves)

# parameters __________________________________________________________________
int_unitwise <- meanSummary(
        average_fisherz,
        c("class", "func", "layer_ordered"), "corr_z"
    )

int_groupwise <- summarySEwithin(
        data = int_unitwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("func", "layer_ordered"), # iv
        idvar = "class"
    )

subjectwise = int_unitwise
subjectwise$layer_ordered <- factor(subjectwise$layer_ordered, levels =  c(
    "conv_1 ablation_impact",
    "conv_2 ablation_impact",
    "conv_3 ablation_impact",
    "conv_4 ablation_impact",
    "conv_5 ablation_impact",
    "dense_1 ablation_impact",
    "dense_2 ablation_impact",
    "conv_1 decoding_accuracy_delta",
    "conv_2 decoding_accuracy_delta",
    "conv_3 decoding_accuracy_delta",
    "conv_4 decoding_accuracy_delta",
    "conv_5 decoding_accuracy_delta",
    "dense_1 decoding_accuracy_delta",
    "dense_2 decoding_accuracy_delta"
  ))
subjectwise$varint <- as.factor(paste(subjectwise$layer_ordered, subjectwise$func))
subjectwise$varint <- factor(subjectwise$varint, 
                             levels = c("mean_cca_corr ablation_impact", "mean_sq_cca_corr ablation_impact", "pwcca ablation_impact", "cka ablation_impact", "procrustes ablation_impact", 
                                        "mean_cca_corr decoding_accuracy_delta", "mean_sq_cca_corr decoding_accuracy_delta", "pwcca decoding_accuracy_delta", "cka decoding_accuracy_delta", "procrustes decoding_accuracy_delta" ))
groupwise = int_groupwise
iv1 = "func"
iv2 = "layer_ordered" 
sub_mean = "mean_per_sub" 
group_mean = "mean_per_sub_norm_mean" 
se = "se" ; subject = "class"
ggtitle = paste0(model_keyword," :: Interaction of functionality and layer" )

legend_title = "Metric"
xlab = "Functionality"
ylab = "Correlation between \nlayer and functionality"
iv_keyword = "int"
dv_keyword = "corr"

# int_color = c(
#   "#000000",
#    "#3F0005",
#    "#7D000B",
#    "#BC0010",
#    "#FA0015",
#    "#000000",
#    "#00003F",
#    "#00007D",
#    "#0000BC",
#    "#0000FA"
# )
int_color = c("#FFECC9","#FFCFA8","#FFB386","#FF9665","#FF7943","#FF5D22",  "#FF4000",
  "#FFECC9",  "#D5E8D2",  "#AAE4DB",  "#80E0E4",  "#55DCED",  "#2BD8F6",  "#00D4FF"
)
bw_color = c("#0F0F0F", "#494949", "#838383", "#BDBDBD", "#F7F7F7")
  # decoding
p3 <- ggplot(data = subjectwise,
            aes(y = .data[[sub_mean]],
                x = .data[[iv1]],
                fill =varint,#.data[[iv2]],# varint, #.data[[iv2]],
                width=.9)) +
  #coord_cartesian(ylim = ylim, expand = TRUE) +
  geom_flat_violin(
    aes(fill = varint),#.data[[iv2]]),
    position = position_nudge(x = .1, y = 0),
    adjust = 1.5,
    trim = FALSE,
    alpha = 0,
    colour = NA
  ) +

  geom_point(
    data = subjectwise,
    aes(
      x = .data[[iv1]],
      y = .data[[sub_mean]],
      #color = interaction(.data[[iv2]],.data[[iv1]])
      color = varint# .data[[iv2]]
    ),
    position = position_jitterdodge(), #position_jitter(width = .05),
    size = 2,
    alpha = 0.8,
    shape = 20, 
    show.legend=FALSE
  ) +

  geom_half_boxplot(
    data = subjectwise,
    aes(x = .data[[iv1]],
        y = .data[[sub_mean]],
        fill = varint),#interaction(metric_ordered,func )),
        #fill = .data[[iv2]]),
      
    side = "r",
    outlier.shape = NA,
    alpha = 0.8,
    width = .8,
    #nudge = 0.2,
    colour = "black",
    #dodge = TRUE,
    # staplelwd = 0,
    notch = FALSE,
    notchwidth = 0,
    varwidth = FALSE,
    errorbar.draw = FALSE,
    center = TRUE,
    show.legend=TRUE
  ) +

  # legend stuff __________________________________________________________________________________ # nolint

  scale_fill_manual(values = int_color, name = "layer", guide = "none") +
  scale_color_manual( values = int_color, name = "layer", guide = "none") +

    guides(fill = "none") +
  guides(color = "none") +
  #guides(fill = guide_legend(title = legend_title)) +
  ggtitle(ggtitle) +
  # coord_flip() + #vertical vs horizontal
  xlab(xlab) +
  ylab(ylab) +
    scale_x_discrete(
    labels = c(
      "ablation_impact" = "Network performance deficits",
      "decoding_accuracy_delta" = "Decoding accuracy deficits"
    )
  ) +
#     scale_fill_discrete(
#     breaks = c("mean_cca_corr ablation_impact", "mean_sq_cca_corr ablation_impact", "pwcca ablation_impact", "cka ablation_impact", "procrustes ablation_impact" ),
#     labels = c("mean_cca_corr","mean_sq_cca_corr", "pwcca", "cka", "procustes"),
#     guide = guide_legend(
#       direction = "horizontal",
#       title.position = "top",
#       label.position = "bottom",
#       label.hjust = 0.5,
#       label.vjust = 1,
#       label.theme = element_text(angle = 90)
#     )
#   )
# +
  # guides(fill =guide_legend(title = legend_title, 
  #                           override.aes = list(shape = 20, size = .5),
  #                           )) + 

  theme_bw() + theme_classic2() +
    #theme(aspect.ratio=4/6) 
theme(aspect.ratio = 6 / 10) +
  theme(legend.position = "none",
        text = element_text(family = "DejaVu Sans"), 
        plot.title = element_text(size=14))


p3
save_fname <-
  file.path(main_dir,'revision',
            'results',
            'figure',
            paste0(model, '03_iv-', iv_keyword, '_dv-', dv_keyword, '.png'))


ggsave(
  save_fname,
  plot = p3,
  width = w,
  #height = h,
  unit = "in",
  dpi = 600,
  scale = 2.5)
```
```


